### 2020-10-28 paper/template/conference_041818.tex
initial commit with NodeTank and the LateX template

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\end{document}

### 2020-10-28 project/src/client/src/bullet.js

@@ -1,0 +1,28 @@
+//defines a bullet object
+game.bullet = function() {
+
+    function setPosition(x, y, z) {
+        this.bulletObj.position.set(x, y, z);
+    }
+
+    function getPosition() {
+        return this.bulletObj.position;
+    }
+
+    function translateX(newX) {
+        this.bulletObj.translateX(newX);
+    }
+
+    function translateZ(newZ) {
+        this.bulletObj.translateZ(newZ);
+    }
+
+    return {
+        bulletObj: undefined,
+        direction: undefined,
+        setPosition: setPosition,
+        getPosition: getPosition,
+        translateX: translateX,
+        translateZ: translateZ
+    }
+};

### 2020-10-28 project/src/client/src/game.js

@@ -1,0 +1,441 @@
+/*
+    Defines an instance of a game - it relies on a socket already being established and passed in at
+    time of instantiation. The idea is to allow the ability to allow multiple instances of the game
+    to run on the same screen,but under different canvases. This makes it easier to run automated tests
+    as I wouldn't have to launch multiple browsers via CLI and pass in messy parameters via the URL.
+
+ */
+
+//Slightly archaic JS, but I like the extra control over the architecture
+//I could have bundled everything with automation tools, but this is easier to set up
+
+//constructor
+//canvas - the target cavas element onto which to render
+//socket - the established socket with which to communicate with the server
+game = function(canvas, socket, token, name) {
+    this.canvas = canvas;
+    this.socket = socket;
+    this.token = token;
+    this.name = name;
+
+    //init world objects to default
+    this.scene = undefined;
+    this.camera = undefined;
+    this.renderer = undefined;
+    this.backgroundMesh = undefined;
+    this.redZone = undefined;
+    this.intersectionPlane = undefined; //Using this as a dummy math object to calculate the intersection of the mouse position
+    this.font = undefined;
+    this.fontMaterial = new THREE.MeshBasicMaterial({color: 0xffffff});
+
+    //contains all elements of a player tank - all player objects spawn off of it
+
+    this.playerTank = undefined;
+    this.otherPlayers = {};
+    this.bullets = {};
+    this.movementVector = new THREE.Vector3(0, 0, 0);
+    this.movementVelocity = 0;// new THREE.Vector3(0, 0, 0); //received from the server
+    this.lastRender = undefined; //the timestamp of the last render loop - use to calculate movement interpolation
+    this.pressedMovementKey = {
+        a: false,
+        d: false,
+        s: false,
+        w: false
+    };
+    this.clicked = false;
+};
+
+game.prototype = {
+    //set up an instance of the game
+    init: function() {
+        console.log("init");
+        console.log(this.canvas);
+        console.log(this.socket);
+        this.configSocket();
+        console.log(this.name);
+        this.socket.emit('joinGame', {
+            token: this.token,
+            name: this.name
+        });
+        //load the typeface font
+        let loader = new THREE.FontLoader();
[…]

### 2020-10-28 project/src/client/src/tank.js

@@ -1,0 +1,50 @@
+//defines a player object
+game.tank = function() {
+    function setLookAt(newLookAt) {
+        this.lookAt = newLookAt;
+        this.gun.lookAt(newLookAt);
+        //this.turretGroup.updateMatrixWorld();
+    }
+
+    function getLookAt() {
+        return this.lookAt;
+    }
+
+    function setPosition(x, y, z) {
+        this.group.position.set(x, y, z);
+    }
+
+    function getPosition() {
+        return this.group.position;
+    }
+
+    function translateX(newX) {
+        this.group.translateX(newX);
+    }
+
+    function translateZ(newZ) {
+        this.group.translateZ(newZ);
+    }
+
+    return {
+        body: undefined,
+        turret: undefined,
+        gun: undefined,
+        position: undefined,
+        lookAt: undefined,
+        linearVelocity: undefined,
+        turretGroup: undefined, //turret will have its own group since lookAt only affects the gun/turret
+        group: undefined, //threejs hierarchy of constituent parts,
+        isAlive: false,
+        xVelocity: 0,
+        yVelocity: 0,
+        text: undefined,
+        score: 0,
+        setLookAt: setLookAt,
+        getLookAt: getLookAt,
+        setPosition: setPosition,
+        getPosition: getPosition,
+        translateX: translateX,
+        translateZ: translateZ
+    }
+};

### 2020-10-28 project/src/server/gameCore/gameLoop.js

@@ -1,0 +1,157 @@
+let three = require("three");
+let socketManager = require("./socket-manager");
+let globalState = require("./global-state");
+let crypto = require("crypto");
+
+let playerTanks = {}; //tracks all player tanks
+let shots = {}; //tracks all shots and their owner
+let lastUpdate = new Date();
+
+//game rules - should really be a separate config
+//note that xmin is defined as being to the left, zMin being at the bottom
+//also note, -Z axis points to the top
+let bounds = {
+    xSpan: 100,
+    zSpan: 100,
+    xMin: -50,
+    xMax: 50,
+    zMax: -50,
+    zMin: 50
+};
+
+let bulletVelocity = 80;
+let movementVelocity = 45;
+
+
+//called for each update from clients
+//note that the position is only set internally in the server
+function updatePlayer(token, packet) {
+    playerTanks[token].lookAt = packet.lookAt;
+    playerTanks[token].movement = packet.movement;
+}
+
+function addTank(token) {
+    playerTanks[token] = {};
+}
+
+function shotTaken(token, lookAt) {
+    //model the object in memory
+    let bGeom = new three.Mesh(new three.SphereGeometry(0.5, 32, 32), new three.MeshBasicMaterial({color: 0x000000}));
+    bGeom.position.set(playerTanks[token].obj.position.x, playerTanks[token].obj.position.y, playerTanks[token].obj.position.z);
+    bGeom.up.set(0, 0, -1);
+    //calculate the direction from the player position to the aim point
+    let direction = new three.Vector3();
+    let aLookAt = new three.Vector3(lookAt.x, lookAt.y, lookAt.z);
+    let bLookAt = new three.Vector3(playerTanks[token].obj.position.x, playerTanks[token].obj.position.y, playerTanks[token].obj.position.z);
+    direction.subVectors(aLookAt, bLookAt).normalize();
+
+    shots[crypto.randomBytes(32).toString("hex")] = {
+        owner: token,
+        obj: bGeom,
+        direction: direction
+    };
+}
+
+//returns a random spawn position on the game map
+function generateSpawnPosition() {
+    let x = Math.floor(Math.random() * (bounds.xSpan - 10)) - (Math.abs(bounds.xMin) - 5);
+    let z = Math.floor(Math.random() * (bounds.zSpan - 10)) - (Math.abs(bounds.zMin) - 5);
+    let y = 5;
+
+    return new three.Vector3(x, y, z);
+}
+
+function checkOutOfBounds() {
+    for (let k in playerTanks) {
[…]

### 2020-10-28 project/src/server/gameCore/global-state.js

@@ -1,0 +1,62 @@
+let currentUsers = 0;
+let maxUsers = 4;
+let userTokens = {};
+let score = {};
+
+function addUser(token, name) {
+    currentUsers += 1;
+    //score needs to have an association with a token, not just the player's name
+    score[token] = {
+        name: name,
+        score: 0
+    };
+}
+
+function getScore() {
+    return score;
+}
+
+function incrementScore(token) {
+    score[token].score += 1;
+}
+
+function decrementScore(token) {
+    score[token].score -= 1;
+}
+
+function getUserCount() {
+    return currentUsers;
+}
+
+function setMaxUsers(m) {
+    maxUsers = m;
+}
+
+function spaceAvailable() {
+    return currentUsers < maxUsers;
+}
+
+function setUserTokens(newUserTokens) {
+    userTokens = newUserTokens;
+}
+
+function getUserTokens() {
+    return userTokens;
+}
+function isTokenValid(token) {
+    return userTokens.hasOwnProperty(token);
+}
+
+
+module.exports = {
+    addUser: addUser,
+    getUserCount: getUserCount,
+    setMaxUsers: setMaxUsers,
+    spaceAvailable: spaceAvailable,
+    setUserTokens: setUserTokens,
+    getUserTokens: getUserTokens,
+    isTokenValid: isTokenValid,
+    incrementScore: incrementScore,
+    decrementScore: decrementScore,
+    getScore: getScore
+};

### 2020-10-28 project/src/server/gameCore/socket-manager.js

@@ -1,0 +1,68 @@
+let globalState = require("../gameCore/global-state");
+let gameLoop = require("./gameLoop");
+let three = require("three");
+
+let socket = undefined;
+let broadcastChan = undefined;
+
+function setUpEvents() {
+    if (socket !== undefined) {
+        socket.on("connection", (socket) => {
+            broadcastChan = socket;
+            console.log("new Connection");
+            socket.on("joinGame", (data) => {
+                console.log("New Player - " + data.name);
+                console.log(globalState.isTokenValid(data.token));
+                if (globalState.isTokenValid(data.token)) {
+                    globalState.addUser(data.token, data.name);
+                    gameLoop.addTank(data.token);
+                    //set starting position on server
+                    let startingPos = gameLoop.generateSpawnPosition();
+                    gameLoop.setInitialPlayerState(data.token, {
+                        movement: new three.Vector3(0, 0,0),
+                        lookAt: new three.Vector3(0, 0,-50),
+                        position: startingPos
+                    }, data.name);
+                    socket.emit("playerStart", {
+                        pos: startingPos,
+                        movementVelocity: 45 //units per second
+                    });
+                }
+            });
+
+            socket.on("playerUpdate", (data) => {
+                //check if the token is valid
+                if (globalState.isTokenValid(data.token)) {
+                    gameLoop.updatePlayer(data.token, data.tankState);
+                }
+            });
+            socket.on("shot", (data) => {
+                //check if the token is valid
+                if (globalState.isTokenValid(data.token)) {
+                    gameLoop.shotTaken(data.token, data.lookAt);
+                }
+            });
+        });
+    }
+}
+
+function broadcast(state) {
+
+    if (broadcastChan !== undefined && globalState.getUserCount() > 0) {
+        //we have to both emit and broadcast in order to ensure everyone gets the updates
+        broadcastChan.broadcast.emit('tick', state);
+        broadcastChan.emit('tick', state);
+    }
+}
+
+
+function setSocket(newSocket) {
+    socket = newSocket;
+    setUpEvents();
+}
+
+
+module.exports = {
+    setSocket: setSocket,
+    broadcast: broadcast
+};

### 2020-10-28 project/src/server/httpServer/server.js

@@ -1,0 +1,50 @@
+function gameServer(gameSettings) {
+    var bodyParser = require("body-parser");
+    var fs = require("fs");
+    var express = require("express");
+    var http = require("http");
+    var globalState = require("../gameCore/global-state");
+    var socketManager = require("../gameCore/socket-manager");
+    var socketio = require('socket.io'); // should be implemented on top of WebSocket directly for better performance
+    var path = require('path');
+
+    globalState.setMaxUsers(gameSettings.gameOptions.maxPlayers);
+
+
+    var app = express();
+    var socketApp = express();
+    var socketHTTP = http.Server(socketApp);
+    var socket = socketio(socketHTTP);
+    socketManager.setSocket(socket);
+
+    //import routes
+    var sessionRoutes = require("../routes/session.js");
+
+    app.use(bodyParser.urlencoded({
+        extended: true
+    }));
+    //allow the use of JSON packets
+    app.use(bodyParser.json());
+    //static file location
+    app.use(express.static(gameSettings.resources));
+
+    //default route
+    app.get("/", function(req, res) {
+        res.sendFile(path.resolve(gameSettings.indexPage));
+    });
+
+    //route for tests
+    app.get("/tests", function(req, res) {
+        res.sendFile(path.resolve(gameSettings.testPage));
+    });
+
+    //map the routes
+    app.use(sessionRoutes);
+
+    var httpServer = http.createServer(app).listen(gameSettings.httpPort);
+    console.log("--Game HTTP Server listening on port: " + gameSettings.httpPort);
+    var socketServer = socketHTTP.listen(gameSettings.socketPort);
+    console.log("--Socket Server listening on port: " + gameSettings.socketPort);
+}
+
+module.exports = gameServer;

### 2020-10-28 project/src/server/init.js

@@ -1,0 +1,26 @@
+var gameHostServer = require("./httpServer/server.js"); //we will use an express server to set up the initial communication/serving static files
+var server;
+
+var serverOptions = {
+    baseURL: global.baseURL,
+    httpPort: 8080, //only providing HTTP, security is not a concern for this project
+    socketPort: 8081, //port to be used by socket.io
+    resources: __dirname + "/../client",
+    indexPage: __dirname + "/../client/index.html",
+    testPage: __dirname + "/../client/test.html",
+    gameOptions: {
+        maxPlayers: 4, //max number of concurrent players
+        rules: { //define the game type and rules associated with it
+            type: "maxPoints",
+            maxPoints: 10
+        }
+    }
+};
+global.baseURL = "http://localhost" + ":" + serverOptions.httpPort;
+
+function init() {
+    server = new gameHostServer(serverOptions);
+}
+
+//kick off the game server
+init();

### 2020-10-28 project/src/server/routes/session.js

@@ -1,0 +1,57 @@
+var express = require("express");
+var router = express.Router();
+var globalState = require("../gameCore/global-state");
+var crypto = require("crypto");
+
+//keeps an array of objects associated a token to a player name
+//the token exists to ensure that only approved socket requests will be allowed through
+var validTokens = {};
+
+router.get("/session/getActivePlayers", function(req, res) {
+    res.writeHead(200, {
+        "Content-Type": "text/plain"
+    });
+    res.end(JSON.stringify({
+        success: true,
+        data: {
+            count: globalState.getUserCount()
+        }
+    }), "utf-8");
+});
+
+
+//This route tells the client whether they can enter the game, if so an unique token is returned
+//which is used by the client to set up the socket
+router.post("/session/createNewSession", function(req, res) {
+    validTokens = globalState.getUserTokens();
+    res.writeHead(200, {
+        "Content-Type": "text/plain"
+    });
+
+    //set name to the empty string if name was not passed
+    var playerName = req.body.playerName === undefined ? "" : req.body.playerName;
+
+    if (globalState.spaceAvailable() && playerName !== "") {
+        var token = crypto.randomBytes(64).toString("hex");
+        validTokens[token] = playerName;
+        syncTokenStates();
+        res.end(JSON.stringify({
+            success: true,
+            data: {
+                token: token //create an unique token that we can reference when the socket is created
+            }
+        }), "utf-8");
+    }
+    else {
+        res.end(JSON.stringify({
+            success: false,
+            message: "Max Number of Players Reached!"
+        }), "utf-8");
+    }
+});
+
+function syncTokenStates() {
+    globalState.setUserTokens(validTokens);
+}
+
+module.exports = router;

### 2020-11-04 paper/PaperDraft2.tex
Added LateX conversion

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Testing Methodologies for a Multiplayer Game Protocol\\
}

\author{\IEEEauthorblockN{Sorin Badila, Cale Campbell, Ryan Wilk}
\IEEEauthorblockA{\textit{Department of Computer Science and Engineering} \\
\textit{Oakland University}\\
Rochester, United States \\
sfbadila@oakland.edu, ccampbell5@oakland.edu, rmwilk@oakland.edu}
}

\maketitle

\begin{abstract}
 Distributed interactive multi-body simulations are an increasingly prevalent breed of software and demand unique strategies with respect to testing. 
 Classically non-networked multiplayer video gaming takes place on a single machine hosting a single local environment within which all players directly 
 control actors in a simulation. Modern networked gaming often requires that a singular environment be remotely hosted with all player-controlled actors and 
 their interactions be distributed to connected client applications.[b] With all these simulations, it is paramount that the individual units in the simulations 
 as well as all the moving parts in the server are rigorously tested. The research gathered for this paper will outline the testing methodologies that we find 
 to be the most significant. Combining strong unit and integration testing inside the server, each simulation needs to be tested for usability, compatibility, and 
 reliability. Likewise, since the integrity of the simulation is paramount, susceptibility to malicious or incorrect information fed into the system  must be mitigated, 
 and as such, we will explore mechanisms by which test the system.

\end{abstract}

\begin{IEEEkeywords}
Testing, Nodejs, networking, multiplayer, WebSocket, software engineering
\end{IEEEkeywords}

\section{Introduction}
In our work we aim to create a testing framework for an online multiplayer javascript application called NodeTank. This application involves two primary components, 
a server, and one or more connected clients. Each client instance renders the play environment to the players as well as a tank object and accepts control inputs from 
a player. Client instances are responsible for forwarding control inputs to the server. The server is responsible for tracking and maintaining state information relevant 
to the gameplay. Various examples of state include health status, position, and orientation. This information needs to be forwarded from the server to the client applications 
with minimal latency in order to provide a continuous stream of snapshots of the game’s state. Client applications are also responsible for recreating and displaying this 
information for the player with the end-goal of providing all players with consistent up-to-date information.

Unit testing can be achieved through traditional means of subjecting applicable functions to predetermined inputs and comparing their results to expected results. 
Functional testing presents a less straight-forward solution. In the basic case, there are two clients and one server, three separate processes that are interacting 
with one another. These interactions can potentially generate a very wide range of outputs and [c][d][e][f][g][h]behaviors of which only a very small subset would be 
considered correct. Not only do the specific actions and reactions between these processes determine program correctness, but the timing between them determine correctness.

\section{Related Works}

The works of Ariurek et al[2] are very interesting to our research because they propose several mechanisms by which to introduce automated test agents into the game
development cycle with the goal of finding defects. They have proposed two mechanisms by which to facilitate this automation; human-like agents and synthetic agents. 
A human-like agent is a separate program which learns the rules and behavior of a game via reinforcement learning. With reinforcement learning, this type of agent would 
learn how a human would play the game as it would have the same reward incentive as a human player, and is thus likely to detect defects which are similar in nature to those 
detected by humans. Their proposed synthetic agent is also a type of program which is trained via reinforcement learning, except its goals are not inline with the goals of a 
real human player. For example, a synthetic agent could be rewarded with implementing a scenario which would be detrimental to winning the game, but which would be likely to
reveal a defect otherwise hidden from expected behavior. Using both of these methods, Ariurek et al have created a system in which the quality of a game could be tested automatically 
and not in a predetermined fashion.

Rezin et al[3] developed a model checking mechanism for a specific multiplayer game. They did so by creating a list of attributes which are mapped to parameters into the model -
 for example, each object must have some position identifier, X/Y/Z as well as a vector which describes the orientation. Our case study, NodeTank, will also suffer from the same 
 problem as their case study in that state explosion due the millions of possible position/orientation combinations and as such the game model must be reduced to meaningfully study it.

Peusaari et al[5] discuss the computational issues and challenges of distributed human-in-the-loop simulations of a basic architecture consisting of several satellite components 
focused around a management component. The specific components include a client, server, motion platform controller, I/O controller, and a manager. The manager distributes setup 
instructions for the simulation as well as collecting and processing data  streams from the other components. The servers play the primary roles of computational units performing 
physics/dynamics processing. The relationship between these client and server components are analogous to the client-server relationship NodeTank utilizes. The piece that we will 
need to construct is the manager, a component that will allow for the distributed initialization of tests and the data collection of those tests. However, in our case, this manager
will observe and report on the behavior code itself rather than sensor data. Components that don’t translate to our work are, with reason, the motion controller. Several of the 
challenges of distributed simulation that are relevant in this paper may be relevant to our work as well. Peusaari outlines the following three main challenges to the distributed 
simulation. The end result of the simulation should be capable of executing in real-time. Secondly, the system, being distributed across a network, will be naturally intolerant of 
delays. The more delay that is introduced, the more the data and validity of the experiment drift. Thirdly data transmissions should be well-planned and organized in such a way that 
minimizes hindrance of the simulation and its core goals. Multi-body simulations require that, at a minimum, coordinates and orientations of bodies subject to physics and dynamics 
calculations be routinely transmitted at reliable intervals.

These are all concerns of NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
 to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.

\subsection{Approach}
Our approach is to develop a testing framework for NodeTank will combine abstract testing of models, unit testing, and functional testing into a single, yet modular, 
utility. The effort of functional testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility 
should be distributable just as the software being tested and a means of distributing and launching a test should be runnable from a single test location. Any data and 
any results of a test run should also be collected and delivered to the single test location where it will be analyzed and classified as either a success or failure. 
Current design will feature the integration of the Labstreaminglayer tool and a Labstreaminglayer server. This tool will allow for the collection of any data or output 
deemed necessary for a given test. It will allow for record sub-millisecond timing of events from multiple machines over a local area network.

For the goal of developing and testing the game locally on one machine, we will also be able to leverage the fact that it is built to run in the browser on
an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated 
system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect 
the state of the simulation on each one of the said client machines independently. This would allow us to inspect the correctness of the model in real time from the 
perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous 
or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.

\section{Background}

As this protocol will work with 3D graphical data, we need to present some prerequisite ideas that the reader may not be
familiar with. Since the purpose of this paper is not to discuss how 3D graphics work, the explanation will be kept brief 
as to only build up the necessary intuition.

\subsection{3D Rendering at a High Level}

In the real world, we have object which we can look at and interact with. When such objects are created in a 3D renderer,
some data must be modeled about the object. For simplicity, we will only consider a Cartesian coordinate system(Fig 4), in which points are mapped 
by numerical coordinates along three perpendicular lines(axes). Intuitively, the positional information may be expressed in terms of a displacement 
along each one of the three axes (X, Y, Z). As such, a simple vector with three components can encode this information(Fig 3.):

\begin{figure}[htbp]
\[ (V_{x}, V_{y}, V_{z}) \]
\caption{Vector Used to Encode Position}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {fig1.png}}
\caption{Example of WebGL Coordinate System}
\end{figure}

However, simply listing the poistion is not sufficient in order to accurately map the object in space. An object may be rotated 
around its position. Fig 4. shows a simple example of a car being rotates about the Z axis. The simplest method by which this information can be encoded 
is to use another three component vector to keep track of the roation around each axis, and then apply each rotation to each axis in a cascading fashion. 
This is commonly known as an Euler Angle, which is intuitive to use, but not sufficent enough in our use case due to the possibility of gimbal lock. 
In short terms, gimbal lock can occur when two axes are in a parallel configuration to each other, which would force an otherwise single axis rotation to instead 
become a composite rotation.

\begin{figure}[htbp]
\centerline{\includegraphics [width = 9cm, height = 5cm] {fig2.png}}
\caption{Example of Rotation Around the Z Axis}
\end{figure}

The conventional solution to this problem is to discard the Euler Angle representation of rotation in favor of using quaternions. 
For the purpose of this paper, we must only know that an equivalent description of orientation can be encoded in a quaternion,
but without the gimbal lock limitation which would cause rotation behavior should it occur. In short, this quaternion may be expressed as a four dimensional
vector, similar to the one expressed in Fig 3., but with an extra component, \textit{w}.

At this point, we have all of the necessary information to encode a static object in our game world, yet there is one more attribute which
must be implemented: velocity. Consider that an object in our game is in motion, assume it is moving along the X axis. If we have enough snapshots of its location,
then we may be able to render its path up until the current snapshot. However, consider what happens until the next snapshot is received; we will have no idea about the object's path. 
In order to circumvent this, information about how fast the object is moving may be encoded such that an extrapolation between snapshots may occur. This velocity attribute 
is split into two segments; the liear velocity, which is the change in position across the Cartesian system, and angular velocity, which is the change in orientation. 
Each one of these attributes may be encoded in a three dimensional vector(Fig 3).

\begin{figure}[htbp]
\begin{equation}
\text {Position:} (V_{x}, V_{y}, V_{z})
\end{equation}
\begin{equation}
\text {Orientation:} (V_{x}, V_{y}, V_{z}, V_{w})
\end{equation}
\begin{equation}
\text {Linear Velocity:} (V_{x}, V_{y}, V_{z})
\end{equation}
\begin{equation}
\text {Angular Velocity:} (V_{x}, V_{y}, V_{z})
\end{equation}
\caption{Complete Object State}
\end{figure}

Fig 6 shows our final object state. This will be our basic building blokc when we will discuss the protocol in detail, 
as this will become the data packet which updates clients on the state of the simulation and the objects therein.

\subsection{Game Model}

The protocol workflow has been described at a very high level, but it is agnostic to the specific game and the rules associated with it. The 
player is modeled by a tank object. This tank object has a few properties associated with it: alive, outOfBounds, score. The alive state 
dictates whether the tank is on the playing field - given that in our rules we have established that being shot simply leads to a respawn, 
this state is only used to indicate that a respawn must occur and that the other player's score is incremented. The outOfBounds attribute is true 
when the player steps outside of the game field, which leads to alive being set to false and score being decremented. The score attribute 
keeps track of the player's current score.

A keen observer would note that a player's tank has many more attributes that those listed above. Rezin et al [3] utilized model checking 
on a multiplayer game, and they came up with an attribute list which contained all variables that would change over the course of the game.
The attributes are tied into parameters, which are constants set at the beginning of the game. For example, a player's tank can be modeled
as a parameter with attrbutes X position, Y position, Z position, lookAt, score, alive, outOfBounds. The limitation of using this approach is that 
if an object's position is utilized in checking the model, the list of all possible state combinations would be too large to ever compute due 
to the size of the game field having granularity in the tens of millions and the total number of possible lookAt locations also being in the millions.

With these considerations in mind, model checking has also been overlooked in favor of utilizing automated testing to test the 
game directly for consistency in its rules. One thing of note is that the formal definition of the game rules for example, a valid x coordinate,
is syntactically equivalent to the check the game logic would perform; therefore writting a model checking program is redundant in this specific 
case. Fig 11 shows the formal definition along with the implementation of the rule.

\begin{figure}[htbp]
\[ (W_{xmin} \leq T_{x} \leq W_{xmax}) \]
\[ !(playerTanks[k].obj.position.x < xMin ||\]
\[ playerTanks[k].obj.position.x > xMax) \]
\caption{Formal Rule and Implementation of Valid X coordinate}
\end{figure}

\section{Implementation}

With the all of the prerequisite work complete, the implementation of the the game and protocol will be discussed. For reference,
the project code is located at (https://github.com/spac3nerd/CSI-5380Proj). The nodejs server 
will need to run both traditional HTTP transactons and socket transactions. The HTTP transactions are used to ask the server if 
there are any open spots in the game, and whether access is granted to a new player. If access is granted, then the server will return 
an unique token to the client with which a socket connection can be requested. The client then requests entry into the game 
with the token and a tunnel is established between the client and the server.

\subsection{Automated Unit Testing}

To be developed

\subsection{Automated Functional Testing}

To be developed

\section{Conclusion}

To be developed

\section{References}
[1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016, 
Available from ProQuest Dissertations & Theses Global. (1881527059). 
Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924

[2] S. Ariyurek, “Automated Video Game Testing Using
Synthetic and Human-Like Agents”, 2019, Available: https://arxiv.org/pdf/1906.00317.pdf

[3] R. Rezin, ”Model Checking in multiplayer games development”, Innopolis University, 
2017, Available: https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=8432324

[4] R. Hofer “DIS Today”, 1995, Available:
https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=400453

[5] J.Peusaari, “Distributed Issues in Real-Time Interactive Simulations”, Department of Technology Lappeenranta University of Technology, Finland,
 Available: https://ieeexplore.ieee.org/abstract/document/5361761
\end{document}

### 2020-11-04 paper/PaperDraft2.tex
Fixed some figure ordering issues

@@
 In the real world, we have object which we can look at and interact with. When such objects are created in a 3D renderer,
-some data must be modeled about the object. For simplicity, we will only consider a Cartesian coordinate system(Fig 4), in which points are mapped 
+some data must be modeled about the object. For simplicity, we will only consider a Cartesian coordinate system(Fig 2), in which points are mapped 
 by numerical coordinates along three perpendicular lines(axes). Intuitively, the positional information may be expressed in terms of a displacement 
-along each one of the three axes (X, Y, Z). As such, a simple vector with three components can encode this information(Fig 3.):
+along each one of the three axes (X, Y, Z). As such, a simple vector with three components can encode this information(Fig 1.):
 
@@
 However, simply listing the poistion is not sufficient in order to accurately map the object in space. An object may be rotated 
-around its position. Fig 4. shows a simple example of a car being rotates about the Z axis. The simplest method by which this information can be encoded 
+around its position. Fig 2. shows a simple example of a car being rotates about the Z axis. The simplest method by which this information can be encoded 
 is to use another three component vector to keep track of the roation around each axis, and then apply each rotation to each axis in a cascading fashion. 
@@
 but without the gimbal lock limitation which would cause rotation behavior should it occur. In short, this quaternion may be expressed as a four dimensional
-vector, similar to the one expressed in Fig 3., but with an extra component, \textit{w}.
+vector, similar to the one expressed in Fig 1., but with an extra component, \textit{w}.
 
@@
 is split into two segments; the liear velocity, which is the change in position across the Cartesian system, and angular velocity, which is the change in orientation. 
-Each one of these attributes may be encoded in a three dimensional vector(Fig 3).
+Each one of these attributes may be encoded in a three dimensional vector(Fig 1).
 
@@
 With the all of the prerequisite work complete, the implementation of the the game and protocol will be discussed. For reference,
-the project code is located at (https://github.com/spac3nerd/CSI-5380Proj). The nodejs server 
+the project code is located at (https://github.com/spac3nerd/CSI-5390Proj). The nodejs server 
 will need to run both traditional HTTP transactons and socket transactions. The HTTP transactions are used to ask the server if 

### 2020-11-04 paper/PaperDraft2.tex
Added latest changes

@@
  control actors in a simulation. Modern networked gaming often requires that a singular environment be remotely hosted with all player-controlled actors and 
- their interactions be distributed to connected client applications.[b] With all these simulations, it is paramount that the individual units in the simulations 
+ their interactions be distributed to connected client applications. With all these simulations, it is paramount that the individual units in the simulations 
  as well as all the moving parts in the server are rigorously tested. The research gathered for this paper will outline the testing methodologies that we find 
@@
 Functional testing presents a less straight-forward solution. In the basic case, there are two clients and one server, three separate processes that are interacting 
-with one another. These interactions can potentially generate a very wide range of outputs and [c][d][e][f][g][h]behaviors of which only a very small subset would be 
+with one another. These interactions can potentially generate a very wide range of outputs and behaviors of which only a very small subset would be 
 considered correct. Not only do the specific actions and reactions between these processes determine program correctness, but the timing between them determine correctness.
@@
 
-\subsection{Approach}
+\section{Approach}
 Our approach is to develop a testing framework for NodeTank will combine abstract testing of models, unit testing, and functional testing into a single, yet modular, 
@@
 
-\subsection{Automated Unit Testing}
-
-To be developed
+In the following sections we will cover the specific testing implementations with the goal of addressing the problem of rigorously testing NodeTank, or any 
+other multiplayer game built on the NodeJS platform.
 
 \subsection{Automated Functional Testing}
+
+The first testing scenario we will consider is to allow the system to automatically play the game in order to test a set of pre-defined set of actions.
+For example, we can programatically interact with the game directly in order to control one of the player tanks. With the system having control over a player character, 
+we can individually test the different aspects of the game: movement, shooting, respawning etc... This type of autmated testing could be invoked on an individual developer's 
+machine in order to test each function of the game as its being developed.
+
+However, we may take this testing even further and consider that since the game runs within the browser, we would be able to tap into any concurrent client simulation. This 
+has the implication that we would be able to inspect the state of each client concurrently.
+
+\subsection{Automated Unit Testing}
 

### 2020-11-30 project/src/server/gameCore/gameLoop.js
Some preparation work for full stack testing

@@ -193,10 +193,30 @@ function loopGame() {
 setInterval( function() {loopGame()}, 1000 / 30);
 
 
+//***Debugging functions
+
+function getSnapshotData() {
+    let gameState = {
+        tanks: {},
+        score: null
+    };
+
+    for (let k in playerTanks) {
+        gameState.tanks[k]["position"] = playerTanks[k].obj.position;
+        gameState.tanks[k]["lookAt"] = playerTanks[k].lookAt;
+        gameState.tanks[k]["name"] = playerTanks[k].name;
+    }
+    gameState.score = globalState.getScore();
+
+    return gameState;
+}
+
+
 module.exports = {
     updatePlayer: updatePlayer,
     addTank: addTank,
     setInitialPlayerState: setInitialPlayerState,
     shotTaken: shotTaken,
-    generateSpawnPosition: generateSpawnPosition
+    generateSpawnPosition: generateSpawnPosition,
+    getSnapshotData: getSnapshotData
 };

### 2020-11-30 project/src/server/httpServer/server.js

@@ -36,7 +36,12 @@ function gameServer(gameSettings) {
 
     //route for tests
     app.get("/unitTesting", function(req, res) {
-        res.sendFile(path.resolve(gameSettings.testPage));
+        res.sendFile(path.resolve(gameSettings.frontEndTests));
+    });
+
+    //route for tests
+    app.get("/fullStackTesting", function(req, res) {
+        res.sendFile(path.resolve(gameSettings.fullStackTests));
     });
 
     //map the routes

### 2020-11-30 project/src/server/init.js

@@ -7,7 +7,8 @@ var serverOptions = {
     socketPort: 8081, //port to be used by socket.io
     resources: __dirname + "/../client",
     indexPage: __dirname + "/../client/index.html",
-    testPage: __dirname + "/../client/unitTesting.html",
+    frontEndTests: __dirname + "/../client/unitTesting.html",
+    fullStackTests: __dirname + "/../client/backEndUnitTesting.html",
     gameOptions: {
         maxPlayers: 4, //max number of concurrent players
         rules: { //define the game type and rules associated with it

### 2020-11-30 project/src/server/routes/debugging.js

@@ -1,16 +1,53 @@
-var express = require("express");
-var router = express.Router();
-var globalState = require("../gameCore/global-state");
+let express = require("express");
+let router = express.Router();
+let globalState = require("../gameCore/global-state");
+let gameLoop = require("../gameCore/gameLoop");
 
 router.post("/debug/reset", function(req, res) {
     res.writeHead(200, {
         "Content-Type": "text/plain"
     });
+    try {
+        globalState.setResetServer(true);
+
+        res.end(JSON.stringify({
+            success: true,
+        }), "utf-8");
+    }
+    catch {
+        res.end(JSON.stringify({
+            success: false
+        }), "utf-8");
+    }
+});
+
+router.post("/debug/getGameState", function(req, res) {
+    res.writeHead(200, {
+        "Content-Type": "text/plain"
+    });
+    try {
+        let snapShot = gameLoop.getSnapshotData();
+
+        res.end(JSON.stringify({
+            success: true,
+            data: snapShot
+        }), "utf-8");
+    }
+    catch {
+        res.end(JSON.stringify({
+            success: false
+        }), "utf-8");
+    }
+
+});
+
+router.post("/debug/getMessageLog", function(req, res) {
+    res.writeHead(200, {
+        "Content-Type": "text/plain"
+    });
     globalState.setResetServer(true)
 
-    res.end(JSON.stringify({
-        success: true,
-    }), "utf-8");
 });
+
 
 module.exports = router;

### 2020-11-30 project/src/client/src/testing/testingFramework.js
Game now plays itself randomly - just need to add verification and sending/receiving messages

@@ -90,5 +90,32 @@ nodeTankTesting.prototype = {
                 callback(data);
             }
         });
+    },
+
+    setRandomMovement: function(gameInstance){
+        //0 - move north, 1 - move south, anything else - none
+        let moveNothSouth = Math.floor(Math.random() * Math.floor(3));
+        //0 - move east, 1 - move west, anything else - none
+        let moveEastWest = Math.floor(Math.random() * Math.floor(3));
+        if (moveNothSouth === 0) {
+            gameInstance.pressedMovementKey.w = true;
+        }
+        if (moveNothSouth === 1) {
+            gameInstance.pressedMovementKey.s = true;
+        }
+        if (moveEastWest === 0) {
+            gameInstance.pressedMovementKey.d = true;
+        }
+        if (moveEastWest === 1) {
+            gameInstance.pressedMovementKey.a = true;
+        }
+    },
+
+    stopAllMovement: function(gameInstance) {
+        gameInstance.pressedMovementKey.w = false;
+        gameInstance.pressedMovementKey.s = false;
+        gameInstance.pressedMovementKey.d = false;
+        gameInstance.pressedMovementKey.a = false;
     }
+
 };

### 2020-11-30 project/src/client/src/testing/testingFramework.js
Finished all test cases - Maybe tomorrow I'll add a case for actually checking the message content, but good enough for now

@@ -67,6 +67,10 @@ nodeTankTesting.prototype = {
         return (variable instanceof expected);
     },
 
+    assertPositionEqual: function(p1, p2) {
+        return (p1.x === p2.x) && (p2.z === p2.z);
+    },
+
 
 
     //Helper functions

### 2020-11-30 project/src/server/gameCore/gameLoop.js

@@ -202,6 +202,7 @@ function getSnapshotData() {
     };
 
     for (let k in playerTanks) {
+        gameState.tanks[k] = {};
         gameState.tanks[k]["position"] = playerTanks[k].obj.position;
         gameState.tanks[k]["lookAt"] = playerTanks[k].lookAt;
         gameState.tanks[k]["name"] = playerTanks[k].name;

### 2020-11-30 project/src/server/gameCore/socket-manager.js

@@ -28,6 +28,9 @@ function setUpEvents() {
                         movementVelocity: 45 //units per second
                     });
                 }
+                else {
+                    console.log(globalState.isTokenValid(data.token));
+                }
             });
 
             socket.on("playerUpdate", (data) => {

### 2020-11-30 project/src/centralData/client.py
Adding supporting thrift files

@@ -1,0 +1,43 @@
+from API.python.PYAgentInterface import *
+import time
+import math
+import threading
+
+import thrift
+from thrift import Thrift
+from thrift.transport import TSocket
+from thrift.transport import TTransport
+from thrift.protocol import TBinaryProtocol
+
+def Connect(ip='127.0.0.1',port=9090):
+    transport = TSocket.TSocket(ip,port)
+    transport = TTransport.TBufferedTransport(transport)
+    protocol = TBinaryProtocol.TBinaryProtocol(transport)
+    client = AgentInterface.Client(protocol)
+    return client,transport
+
+
+def LoopConnect(state):
+    while(not state[0]):
+        try:
+            client,tx = Connect()
+            tx.open()
+            state[1] = True
+            print("Success...")
+            state[2],state[3] = client,tx
+            break
+        except Exception as ex:
+            pass
+        time.sleep(1)
+        print("trying again...")
+    print("Returning...")
+
+def TryConnect():
+    stopper = [False,False,None,None]
+    trd = threading.Thread(target=LoopConnect,args=(stopper,))
+    trd.start()
+    return stopper,trd
+
+if(__name__=='__main__'):
+    client,tx = Connect()
+    tx.open()

### 2020-11-30 project/src/centralData/example.py

@@ -1,0 +1,27 @@
+from client import TryConnect,Connect
+from Preprocessing.imageProcessing import PreProcess,CVShow,DisplayStream
+import time
+
+TEST_NAME = "name"
+
+# results,thread = TryConnect()
+#
+# while(results[1]==False):
+#     time.sleep(1)
+
+client,tx = Connect()
+tx.open()
+
+token = client.GetTokenByName(TEST_NAME)
+
+images = []
+
+def ShowNow(xscale=1.0,yscale=1.0):
+    d = client.GetImageData(token)
+    while(len(d)==0):
+        d = client.GetImageData(token)
+        time.sleep(.1)
+    f = PreProcess(d,xscale,yscale)
+    print("shape: {}".format(f.shape))
+    images.append(f)
+    CVShow(f)

### 2020-11-30 project/src/centralData/API/nodejs/AgentInterface.js
Adding centralData directory

@@ -1,0 +1,1398 @@
+//
+// Autogenerated by Thrift Compiler (0.13.0)
+//
+// DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+//
+"use strict";
+
+var thrift = require('thrift');
+var Thrift = thrift.Thrift;
+var Q = thrift.Q;
+var Int64 = require('node-int64');
+
+
+var ttypes = require('./jstest_types');
+//HELPER FUNCTIONS AND STRUCTURES
+
+var AgentInterface_GetTokenByName_args = function(args) {
+  this.name = null;
+  if (args) {
+    if (args.name !== undefined && args.name !== null) {
+      this.name = args.name;
+    }
+  }
+};
+AgentInterface_GetTokenByName_args.prototype = {};
+AgentInterface_GetTokenByName_args.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    var fid = ret.fid;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    switch (fid) {
+      case 1:
+      if (ftype == Thrift.Type.STRING) {
+        this.name = input.readString();
+      } else {
+        input.skip(ftype);
+      }
+      break;
+      case 0:
+        input.skip(ftype);
+        break;
+      default:
+        input.skip(ftype);
+    }
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+AgentInterface_GetTokenByName_args.prototype.write = function(output) {
+  output.writeStructBegin('AgentInterface_GetTokenByName_args');
+  if (this.name !== null && this.name !== undefined) {
+    output.writeFieldBegin('name', Thrift.Type.STRING, 1);
+    output.writeString(this.name);
+    output.writeFieldEnd();
+  }
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
+var AgentInterface_GetTokenByName_result = function(args) {
+  this.success = null;
+  if (args) {
+    if (args.success !== undefined && args.success !== null) {
+      this.success = args.success;
+    }
+  }
+};
+AgentInterface_GetTokenByName_result.prototype = {};
+AgentInterface_GetTokenByName_result.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    var fid = ret.fid;
[…]

### 2020-11-30 project/src/centralData/API/python/PYAgentInterface/AgentInterface.py

@@ -1,0 +1,1371 @@
+#
+# Autogenerated by Thrift Compiler (0.13.0)
+#
+# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+#
+#  options string: py
+#
+
+from thrift.Thrift import TType, TMessageType, TFrozenDict, TException, TApplicationException
+from thrift.protocol.TProtocol import TProtocolException
+from thrift.TRecursive import fix_spec
+
+import sys
+import logging
+from .ttypes import *
+from thrift.Thrift import TProcessor
+from thrift.transport import TTransport
+all_structs = []
+
+
+class Iface(object):
+    def GetTokenByName(self, name):
+        """
+        Parameters:
+         - name
+
+        """
+        pass
+
+    def SetLookAt(self, token, direction):
+        """
+        Parameters:
+         - token
+         - direction
+
+        """
+        pass
+
+    def SetMove(self, token, x, y, z):
+        """
+        Parameters:
+         - token
+         - x
+         - y
+         - z
+
+        """
+        pass
+
+    def Fire(self, token):
+        """
+        Parameters:
+         - token
+
+        """
+        pass
+
+    def GetSceneData(self, token):
+        """
+        Parameters:
+         - token
+
+        """
+        pass
+
+    def GetImageData(self, token):
+        """
+        Parameters:
+         - token
+
+        """
+        pass
+
+    def GetPose(self, token):
+        """
+        Parameters:
+         - token
+
+        """
+        pass
+
+
+class Client(Iface):
+    def __init__(self, iprot, oprot=None):
+        self._iprot = self._oprot = iprot
+        if oprot is not None:
+            self._oprot = oprot
+        self._seqid = 0
+
+    def GetTokenByName(self, name):
+        """
+        Parameters:
+         - name
+
+        """
+        self.send_GetTokenByName(name)
+        return self.recv_GetTokenByName()
+
+    def send_GetTokenByName(self, name):
+        self._oprot.writeMessageBegin('GetTokenByName', TMessageType.CALL, self._seqid)
+        args = GetTokenByName_args()
+        args.name = name
+        args.write(self._oprot)
+        self._oprot.writeMessageEnd()
+        self._oprot.trans.flush()
+
+    def recv_GetTokenByName(self):
+        iprot = self._iprot
+        (fname, mtype, rseqid) = iprot.readMessageBegin()
+        if mtype == TMessageType.EXCEPTION:
[…]

### 2020-11-30 project/src/centralData/API/python/PYAgentInterface/__init__.py

@@ -1,0 +1,1 @@
+__all__ = ['ttypes', 'constants', 'AgentInterface']

### 2020-11-30 project/src/centralData/API/python/PYAgentInterface/ttypes.py

@@ -1,0 +1,282 @@
+#
+# Autogenerated by Thrift Compiler (0.13.0)
+#
+# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+#
+#  options string: py
+#
+
+from thrift.Thrift import TType, TMessageType, TFrozenDict, TException, TApplicationException
+from thrift.protocol.TProtocol import TProtocolException
+from thrift.TRecursive import fix_spec
+
+import sys
+
+from thrift.transport import TTransport
+all_structs = []
+
+
+class ButtonStates(object):
+    """
+    Attributes:
+     - WDown
+     - ADown
+     - SDown
+     - DDown
+
+    """
+
+
+    def __init__(self, WDown=False, ADown=False, SDown=False, DDown=False,):
+        self.WDown = WDown
+        self.ADown = ADown
+        self.SDown = SDown
+        self.DDown = DDown
+
+    def read(self, iprot):
+        if iprot._fast_decode is not None and isinstance(iprot.trans, TTransport.CReadableTransport) and self.thrift_spec is not None:
+            iprot._fast_decode(self, iprot, [self.__class__, self.thrift_spec])
+            return
+        iprot.readStructBegin()
+        while True:
+            (fname, ftype, fid) = iprot.readFieldBegin()
+            if ftype == TType.STOP:
+                break
+            if fid == 1:
+                if ftype == TType.BOOL:
+                    self.WDown = iprot.readBool()
+                else:
+                    iprot.skip(ftype)
+            elif fid == 2:
+                if ftype == TType.BOOL:
+                    self.ADown = iprot.readBool()
+                else:
+                    iprot.skip(ftype)
+            elif fid == 3:
+                if ftype == TType.BOOL:
+                    self.SDown = iprot.readBool()
+                else:
+                    iprot.skip(ftype)
+            elif fid == 4:
+                if ftype == TType.BOOL:
+                    self.DDown = iprot.readBool()
+                else:
+                    iprot.skip(ftype)
+            else:
+                iprot.skip(ftype)
+            iprot.readFieldEnd()
+        iprot.readStructEnd()
+
+    def write(self, oprot):
+        if oprot._fast_encode is not None and self.thrift_spec is not None:
+            oprot.trans.write(oprot._fast_encode(self, [self.__class__, self.thrift_spec]))
+            return
[…]

### 2020-11-30 project/src/server/gameCore/gameLoop.js
Adding DataState structure and thift imports

@@ -3,6 +3,12 @@ let socketManager = require("./socket-manager");
 let globalState = require("./global-state");
 let crypto = require("crypto");
 
+const {Worker,isMainThread,parentPort} = require("worker_threads");
+
+let thrift     = require("thrift");
+let aInterface = require("../../centralData/API/nodejs/AgentInterface");
+let ttypes     = require("../../centralData/API/nodejs/jstest_types");
+
 let playerTanks = {}; //tracks all player tanks
 let shots = {}; //tracks all shots and their owner
 let lastUpdate = new Date();
@@ -23,6 +29,14 @@ let bounds = {
 let bulletVelocity = 130;
 let movementVelocity = 70;
 
+
+let DataState = {
+  'agentToken':  undefined,
+  'agentLookat': new three.Vector3(0,0,0),
+  'agentMove':   new three.Vector(0,0,0),
+  'goManual':    true,
+  'lastImage':   ""
+}
 
 //called for each update from clients
 //note that the position is only set internally in the server

### 2020-11-30 project/src/server/gameCore/gameLoop.js
adding thrift server

@@ -226,6 +226,89 @@ function getSnapshotData() {
     return gameState;
 }
 
+var GetTokenByNameFunc = function(name)
+{
+  console.log('GetTokenByName called...')
+  for (let k in playerTanks)
+  {
+    if(playerTanks[k].name === name)
+    {
+      agentToken = k;
+      let socketManager = require("./socket-manager");
+      socketManager.flagSource(agentToken);
+      return agentToken;
+    }
+  }
+  return "[NONE]";
+}
+
+var SetLookAtFunc = function(token,point)
+{
+  agentLookat = new three.Vector3(point.x,point.y,point.z);
+  playerTanks[token].lookAt = agentLookat;
+  updatePlayer(token,playerTanks[token]);
+  console.log(point);
+  console.log("SetLookat");
+}
+var FireFunc = function(token)
+{
+  shotTaken(agentToken,playerTanks[agentToken].lookAt);
+  console.log("Fire called...");
+}
+
+var SetMoveFunc = function(token,x,y,z)
+{
+  console.log("SetMove called...");
+  var movement = new three.Vector3(x,y,z);
+  goManual = false;
+  if(x===0.0 && y===0.0 && z===0.0) {
+    goManual=true;
+  }
+  movement.normalize();
+  agentMove = movement;
+  console.log(movement);
+}
+
+var GetSceneDataFunc = function(token)
+{
+  console.log("GetSceneDataFunc called...")
+  return "thisissomestring"
+}
+
+var GetImageData = function(token){
+  console.log("calling GetImageData");
+  if(token === agentToken){
+    let socketManager = require("./socket-manager");
+    img = socketManager.getImageData();
+    return img;
+  }
+}
+
+var GetPoseFunc = function(token)
+{
+  var pos = playerTanks[token].obj.position;
+  var lat = playerTanks[token].lookAt;
+
+  var a = new ttypes.Point({x:pos.x,y:pos.y,z:pos.z});
+  var b = new ttypes.Point({x:lat.x,y:lat.y,z:lat.z});
+
+  console.log("GetPoseFunc called...");
+
+  return new ttypes.Pose({pos:a,ori:b});
+}
+let thriftServer = thrift.createServer(aInterface,{
+  SetLookAt:      SetLookAtFunc,
+  GetTokenByName: GetTokenByNameFunc,
+  GetSceneData:   GetSceneDataFunc,
+  SetMove:        SetMoveFunc,
[…]

### 2020-11-30 project/src/server/gameCore/gameLoop.js
Continued thrift control support

@@ -161,14 +161,28 @@ function loopGame() {
     //go through all players and update the location
     for (let k in playerTanks) {
         if (playerTanks[k].movement !== undefined) {
-            let mV = new three.Vector3(playerTanks[k].movement.x, playerTanks[k].movement.y, playerTanks[k].movement.z).normalize(); //normalize this vector to prevent any shenanigans
-            playerTanks[k].obj.translateX((mV.x * movementVelocity) * delta);
-            playerTanks[k].obj.translateZ((mV.z * movementVelocity) * delta);
-            newPlayerState[k] = {
-                position: playerTanks[k].obj.position,
-                lookAt: playerTanks[k].lookAt,
-                name: playerTanks[k].name
-            };
+          let mV = new three.Vector3(playerTanks[k].movement.x, playerTanks[k].movement.y, playerTanks[k].movement.z).normalize(); //normalize this vector to prevent any shenanigans
+          if(k===DataState.agentToken && DataState.goManual === false){
+            mV = DataState.agentMove;
+          }
+          playerTanks[k].obj.translateX((mV.x * movementVelocity) * delta);
+          playerTanks[k].obj.translateZ((mV.z * movementVelocity) * delta);
+            if(k === DataState.agentToken)
+            {
+              newPlayerState[k] = {
+                  position: playerTanks[k].obj.position,
+                  lookAt: DataState.agentLookat,
+                  name: playerTanks[k].name
+              };
+            }
+            else
+            {
+              newPlayerState[k] = {
+                  position: playerTanks[k].obj.position,
+                  lookAt: playerTanks[k].lookAt,
+                  name: playerTanks[k].name
+              };
+            }
         }
     }
 
@@ -233,10 +247,10 @@ var GetTokenByNameFunc = function(name)
   {
     if(playerTanks[k].name === name)
     {
-      agentToken = k;
+      DataState.agentToken = k;
       let socketManager = require("./socket-manager");
-      socketManager.flagSource(agentToken);
-      return agentToken;
+      socketManager.flagSource(DataState.agentToken);
+      return DataState.agentToken;
     }
   }
   return "[NONE]";
@@ -244,15 +258,15 @@ var GetTokenByNameFunc = function(name)
 
 var SetLookAtFunc = function(token,point)
 {
[…]

### 2020-11-30 project/src/server/gameCore/socket-manager.js

@@ -5,6 +5,8 @@ let three = require("three");
 let socket = undefined;
 let broadcastChan = undefined;
 
+let iamgeData = "";
+
 function setUpEvents() {
     if (socket !== undefined) {
         socket.on("connection", (socket) => {
@@ -69,8 +71,22 @@ function setSocket(newSocket) {
     setUpEvents();
 }
 
+// Flag user with given token as source of image data:
+function flagDataSource(userToken) {
+  if (broadcastChan !== undefined && globalState.getUserCount() > 0){
+    broadcastChan.broadcast.emit("flagSource",userToken);
+    broadcastChan.emit("flagSource",userToken);
+  }
+}
+
+// Return last received image data:
+function getImageData(){
+  return imageData;
+}
 
 module.exports = {
     setSocket: setSocket,
-    broadcast: broadcast
+    broadcast: broadcast,
+    flagSource: flagDataSource,
+    getImageData: getImageData
 };

### 2020-11-30 project/src/server/gameCore/gameLoop.js
typo

@@ -33,7 +33,7 @@ let movementVelocity = 70;
 let DataState = {
   'agentToken':  undefined,
   'agentLookat': new three.Vector3(0,0,0),
-  'agentMove':   new three.Vector(0,0,0),
+  'agentMove':   new three.Vector3(0,0,0),
   'goManual':    true,
   'lastImage':   ""
 }

### 2020-11-30 project/src/server/gameCore/socket-manager.js
typo fix

@@ -5,7 +5,7 @@ let three = require("three");
 let socket = undefined;
 let broadcastChan = undefined;
 
-let iamgeData = "";
+let imageData = "";
 
 function setUpEvents() {
     if (socket !== undefined) {

### 2020-11-30 project/src/server/gameCore/gameLoop.js
Adding image transfer

@@ -290,7 +290,6 @@ var GetSceneDataFunc = function(token)
 }
 
 var GetImageData = function(token){
-  console.log("calling GetImageData");
   if(token === DataState.agentToken){
     let socketManager = require("./socket-manager");
     img = socketManager.getImageData();

### 2020-11-30 project/src/server/gameCore/socket-manager.js

@@ -50,7 +50,7 @@ function setUpEvents() {
 
             //Cale - screenshot is received here
             socket.on("screenShotSent", (data) => {
-                console.log(data);
+                imageData = data;
             });
         });
     }

### 2020-11-30 agentIF/API/nodejs/AgentInterface.js
removing old, unnecessary directory

@@ -1,685 +1,0 @@
-//
-// Autogenerated by Thrift Compiler (0.13.0)
-//
-// DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
-//
-"use strict";
-
-var thrift = require('thrift');
-var Thrift = thrift.Thrift;
-var Q = thrift.Q;
-var Int64 = require('node-int64');
-
-
-var ttypes = require('./jstest_types');
-//HELPER FUNCTIONS AND STRUCTURES
-
-var AgentInterface_SetButtons_args = function(args) {
-  this.buttons = null;
-  if (args) {
-    if (args.buttons !== undefined && args.buttons !== null) {
-      this.buttons = new ttypes.ButtonStates(args.buttons);
-    }
-  }
-};
-AgentInterface_SetButtons_args.prototype = {};
-AgentInterface_SetButtons_args.prototype.read = function(input) {
-  input.readStructBegin();
-  while (true) {
-    var ret = input.readFieldBegin();
-    var ftype = ret.ftype;
-    var fid = ret.fid;
-    if (ftype == Thrift.Type.STOP) {
-      break;
-    }
-    switch (fid) {
-      case 1:
-      if (ftype == Thrift.Type.STRUCT) {
-        this.buttons = new ttypes.ButtonStates();
-        this.buttons.read(input);
-      } else {
-        input.skip(ftype);
-      }
-      break;
-      case 0:
-        input.skip(ftype);
-        break;
-      default:
-        input.skip(ftype);
-    }
-    input.readFieldEnd();
-  }
-  input.readStructEnd();
-  return;
-};
-
-AgentInterface_SetButtons_args.prototype.write = function(output) {
-  output.writeStructBegin('AgentInterface_SetButtons_args');
-  if (this.buttons !== null && this.buttons !== undefined) {
-    output.writeFieldBegin('buttons', Thrift.Type.STRUCT, 1);
-    this.buttons.write(output);
-    output.writeFieldEnd();
-  }
-  output.writeFieldStop();
-  output.writeStructEnd();
-  return;
-};
-
-var AgentInterface_SetButtons_result = function(args) {
-};
-AgentInterface_SetButtons_result.prototype = {};
-AgentInterface_SetButtons_result.prototype.read = function(input) {
-  input.readStructBegin();
-  while (true) {
-    var ret = input.readFieldBegin();
-    var ftype = ret.ftype;
[…]

### 2020-11-30 project/src/centralData/API/Data/nodejs/DataInterface.js
adding support for second RPC family

@@ -1,0 +1,544 @@
+//
+// Autogenerated by Thrift Compiler (0.13.0)
+//
+// DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+//
+"use strict";
+
+var thrift = require('thrift');
+var Thrift = thrift.Thrift;
+var Q = thrift.Q;
+var Int64 = require('node-int64');
+
+
+var ttypes = require('./data_types');
+//HELPER FUNCTIONS AND STRUCTURES
+
+var DataInterface_GetGameData_args = function(args) {
+  this.jsonData = null;
+  if (args) {
+    if (args.jsonData !== undefined && args.jsonData !== null) {
+      this.jsonData = args.jsonData;
+    }
+  }
+};
+DataInterface_GetGameData_args.prototype = {};
+DataInterface_GetGameData_args.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    var fid = ret.fid;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    switch (fid) {
+      case 1:
+      if (ftype == Thrift.Type.STRING) {
+        this.jsonData = input.readString();
+      } else {
+        input.skip(ftype);
+      }
+      break;
+      case 0:
+        input.skip(ftype);
+        break;
+      default:
+        input.skip(ftype);
+    }
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+DataInterface_GetGameData_args.prototype.write = function(output) {
+  output.writeStructBegin('DataInterface_GetGameData_args');
+  if (this.jsonData !== null && this.jsonData !== undefined) {
+    output.writeFieldBegin('jsonData', Thrift.Type.STRING, 1);
+    output.writeString(this.jsonData);
+    output.writeFieldEnd();
+  }
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
+var DataInterface_GetGameData_result = function(args) {
+  this.success = null;
+  if (args) {
+    if (args.success !== undefined && args.success !== null) {
+      this.success = args.success;
+    }
+  }
+};
+DataInterface_GetGameData_result.prototype = {};
+DataInterface_GetGameData_result.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
[…]

### 2020-11-30 project/src/centralData/API/Data/python/PYDataInterface/DataInterface.py

@@ -1,0 +1,541 @@
+#
+# Autogenerated by Thrift Compiler (0.13.0)
+#
+# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+#
+#  options string: py
+#
+
+from thrift.Thrift import TType, TMessageType, TFrozenDict, TException, TApplicationException
+from thrift.protocol.TProtocol import TProtocolException
+from thrift.TRecursive import fix_spec
+
+import sys
+import logging
+from .ttypes import *
+from thrift.Thrift import TProcessor
+from thrift.transport import TTransport
+all_structs = []
+
+
+class Iface(object):
+    def GetGameData(self, jsonData):
+        """
+        Parameters:
+         - jsonData
+
+        """
+        pass
+
+    def ExecuteTests(self):
+        pass
+
+    def GetTestResults(self):
+        pass
+
+
+class Client(Iface):
+    def __init__(self, iprot, oprot=None):
+        self._iprot = self._oprot = iprot
+        if oprot is not None:
+            self._oprot = oprot
+        self._seqid = 0
+
+    def GetGameData(self, jsonData):
+        """
+        Parameters:
+         - jsonData
+
+        """
+        self.send_GetGameData(jsonData)
+        return self.recv_GetGameData()
+
+    def send_GetGameData(self, jsonData):
+        self._oprot.writeMessageBegin('GetGameData', TMessageType.CALL, self._seqid)
+        args = GetGameData_args()
+        args.jsonData = jsonData
+        args.write(self._oprot)
+        self._oprot.writeMessageEnd()
+        self._oprot.trans.flush()
+
+    def recv_GetGameData(self):
+        iprot = self._iprot
+        (fname, mtype, rseqid) = iprot.readMessageBegin()
+        if mtype == TMessageType.EXCEPTION:
+            x = TApplicationException()
+            x.read(iprot)
+            iprot.readMessageEnd()
+            raise x
+        result = GetGameData_result()
+        result.read(iprot)
+        iprot.readMessageEnd()
+        if result.success is not None:
+            return result.success
+        raise TApplicationException(TApplicationException.MISSING_RESULT, "GetGameData failed: unknown result")
+
+    def ExecuteTests(self):
+        self.send_ExecuteTests()
+        self.recv_ExecuteTests()
+
+    def send_ExecuteTests(self):
[…]

### 2020-11-30 project/src/centralData/client.py

@@ -1,4 +1,4 @@
-from API.python.PYAgentInterface import *
+from API.RemoteCtrl.python.PYAgentInterface import *
 import time
 import math
 import threading

### 2020-11-30 project/src/server/gameCore/gameLoop.js

@@ -6,8 +6,9 @@ let crypto = require("crypto");
 const {Worker,isMainThread,parentPort} = require("worker_threads");
 
 let thrift     = require("thrift");
-let aInterface = require("../../centralData/API/nodejs/AgentInterface");
-let ttypes     = require("../../centralData/API/nodejs/jstest_types");
+let aInterface = require("../../centralData/API/RemoteCtrl/nodejs/AgentInterface");
+let ttypes     = require("../../centralData/API/RemoteCtrl/nodejs/jstest_types");
+let dataInterface = require("../../centralData/API/Data/nodejs/DataInterface");
 
 let playerTanks = {}; //tracks all player tanks
 let shots = {}; //tracks all shots and their owner
@@ -318,8 +319,18 @@ let thriftServer = thrift.createServer(aInterface,{
   GetPose:        GetPoseFunc,
   Fire:           FireFunc
 });
+dataServer = thrift.createServer(dataInterface,{
+  GetGameData: function(json){},
+  ExecuteTests: function(){},
+  GetTestRestults: function(){return "thisString";}
+});
 if(isMainThread)
 {
+  const {Worker2,isMainThread2,parentPort2} = require("worker_threads");
+  if(isMainThread2)
+  {
+
+  }
   thriftServer.listen(9090);
 }
 

### 2020-12-01 project/src/centralData/API/RemoteCtrl/nodejs/AgentInterface.js
updating control api

@@ -699,6 +699,81 @@ AgentInterface_GetPose_result.prototype.write = function(output) {
   return;
 };
 
+var AgentInterface_StartDataServer_args = function(args) {
+  this.portno = null;
+  if (args) {
+    if (args.portno !== undefined && args.portno !== null) {
+      this.portno = args.portno;
+    }
+  }
+};
+AgentInterface_StartDataServer_args.prototype = {};
+AgentInterface_StartDataServer_args.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    var fid = ret.fid;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    switch (fid) {
+      case 1:
+      if (ftype == Thrift.Type.I16) {
+        this.portno = input.readI16();
+      } else {
+        input.skip(ftype);
+      }
+      break;
+      case 0:
+        input.skip(ftype);
+        break;
+      default:
+        input.skip(ftype);
+    }
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+AgentInterface_StartDataServer_args.prototype.write = function(output) {
+  output.writeStructBegin('AgentInterface_StartDataServer_args');
+  if (this.portno !== null && this.portno !== undefined) {
+    output.writeFieldBegin('portno', Thrift.Type.I16, 1);
+    output.writeI16(this.portno);
+    output.writeFieldEnd();
+  }
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
+var AgentInterface_StartDataServer_result = function(args) {
+};
+AgentInterface_StartDataServer_result.prototype = {};
+AgentInterface_StartDataServer_result.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    input.skip(ftype);
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+AgentInterface_StartDataServer_result.prototype.write = function(output) {
+  output.writeStructBegin('AgentInterface_StartDataServer_result');
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
 var AgentInterfaceClient = exports.Client = function(output, pClass) {
   this.output = output;
   this.pClass = pClass;
[…]

### 2020-12-01 project/src/centralData/API/RemoteCtrl/python/PYAgentInterface/AgentInterface.py

@@ -79,6 +79,14 @@ class Iface(object):
         """
         pass
 
+    def StartDataServer(self, portno):
+        """
+        Parameters:
+         - portno
+
+        """
+        pass
+
 
 class Client(Iface):
     def __init__(self, iprot, oprot=None):
@@ -313,6 +321,36 @@ class Client(Iface):
             return result.success
         raise TApplicationException(TApplicationException.MISSING_RESULT, "GetPose failed: unknown result")
 
+    def StartDataServer(self, portno):
+        """
+        Parameters:
+         - portno
+
+        """
+        self.send_StartDataServer(portno)
+        self.recv_StartDataServer()
+
+    def send_StartDataServer(self, portno):
+        self._oprot.writeMessageBegin('StartDataServer', TMessageType.CALL, self._seqid)
+        args = StartDataServer_args()
+        args.portno = portno
+        args.write(self._oprot)
+        self._oprot.writeMessageEnd()
+        self._oprot.trans.flush()
+
+    def recv_StartDataServer(self):
+        iprot = self._iprot
+        (fname, mtype, rseqid) = iprot.readMessageBegin()
+        if mtype == TMessageType.EXCEPTION:
+            x = TApplicationException()
+            x.read(iprot)
+            iprot.readMessageEnd()
+            raise x
+        result = StartDataServer_result()
+        result.read(iprot)
+        iprot.readMessageEnd()
+        return
+
 
 class Processor(Iface, TProcessor):
     def __init__(self, handler):
@@ -325,6 +363,7 @@ class Processor(Iface, TProcessor):
         self._processMap["GetSceneData"] = Processor.process_GetSceneData
         self._processMap["GetImageData"] = Processor.process_GetImageData
         self._processMap["GetPose"] = Processor.process_GetPose
+        self._processMap["StartDataServer"] = Processor.process_StartDataServer
         self._on_message_begin = None
 
     def on_message_begin(self, func):
@@ -504,6 +543,29 @@ class Processor(Iface, TProcessor):
             msg_type = TMessageType.EXCEPTION
             result = TApplicationException(TApplicationException.INTERNAL_ERROR, 'Internal error')
         oprot.writeMessageBegin("GetPose", msg_type, seqid)
+        result.write(oprot)
+        oprot.writeMessageEnd()
+        oprot.trans.flush()
+
+    def process_StartDataServer(self, seqid, iprot, oprot):
+        args = StartDataServer_args()
+        args.read(iprot)
[…]

### 2020-12-01 project/src/server/gameCore/gameLoop.js
adding dataserver to gameloop.js

@@ -241,6 +241,12 @@ function getSnapshotData() {
     return gameState;
 }
 
+dataServer = thrift.createServer(dataInterface,{
+  GetGameData: function(json){},
+  ExecuteTests: function(){},
+  GetTestRestults: function(){return "thisString";}
+});
+
 var GetTokenByNameFunc = function(name)
 {
   console.log('GetTokenByName called...')
@@ -310,6 +316,17 @@ var GetPoseFunc = function(token)
 
   return new ttypes.Pose({pos:a,ori:b});
 }
+
+var StartDataServerFunc = function(inPort)
+{
+  const {Worker2,isMainThread2,parentPort2} = require("worker_threads");
+  if(!isMainThread2)
+  {
+    console.log("data listening");
+    dataServer.listen(inPort);
+  }
+}
+
 let thriftServer = thrift.createServer(aInterface,{
   SetLookAt:      SetLookAtFunc,
   GetTokenByName: GetTokenByNameFunc,
@@ -317,20 +334,12 @@ let thriftServer = thrift.createServer(aInterface,{
   SetMove:        SetMoveFunc,
   GetImageData:   GetImageData,
   GetPose:        GetPoseFunc,
-  Fire:           FireFunc
-});
-dataServer = thrift.createServer(dataInterface,{
-  GetGameData: function(json){},
-  ExecuteTests: function(){},
-  GetTestRestults: function(){return "thisString";}
+  Fire:           FireFunc,
+  StartDataServer:StartDataServerFunc
 });
 if(isMainThread)
 {
-  const {Worker2,isMainThread2,parentPort2} = require("worker_threads");
-  if(isMainThread2)
-  {
-
-  }
+  console.log("Ctrl listening");
   thriftServer.listen(9090);
 }
 

### 2020-12-01 project/src/centralData/Clients/ControlClient.py
Updating Data and Control clients, adding exception handling to thrift servers in gameLoop.js

@@ -1,0 +1,21 @@
+from .ThriftCommon import *
+
+import sys
+sys.path.append("..")
+
+import API
+from API.RemoteCtrl.python.PYAgentInterface import *
+import time
+import math
+import threading
+
+class Control(object):
+    def __init__(self,IPAddr='127.0.0.1',port=9090):
+        self.DefaultPortNo = port
+        self.DefaultIp     = IPAddr
+    def Connect(ip=self.DefaultPortNo,port=self.DefauoltPortNo):
+        transport = TSocket.TSocket(ip,port)
+        transport = TTransport.TBufferedTransport(transport)
+        protocol  = TBinaryProtocol.TBinaryProtocol(transport)
+        client    = AgentInterface.Client(protocol)
+        return client,transport

### 2020-12-01 project/src/centralData/Clients/DataClient.py

@@ -1,0 +1,21 @@
+from .ThriftCommon import *
+
+import sys
+sys.path.append("..")
+
+import API
+from API.Data.python.PYDataInterface import *
+import time
+import math
+import threading
+
+class Data(object):
+    def __init__(self,IPAddr='127.0.0.1',port=9091):
+        self.DefaultPortNo = port
+        self.DefaultIp     = IPAddr
+    def Connect(ip=self.DefaultPortNo,port=self.DefauoltPortNo):
+        transport = TSocket.TSocket(ip,port)
+        transport = TTransport.TBufferedTransport(transport)
+        protocol  = TBinaryProtocol.TBinaryProtocol(transport)
+        client    = AgentInterface.Client(protocol)
+        return client,transport

### 2020-12-01 project/src/centralData/Clients/ThriftCommon.py

@@ -1,0 +1,5 @@
+import thrift
+from thrift import Thrift
+from thrift.transport import TSocket
+from thrift.transport import TTransport
+from thrift.protocol import TBinaryProtocol

### 2020-12-01 project/src/server/gameCore/gameLoop.js

@@ -323,7 +323,12 @@ var StartDataServerFunc = function(inPort)
   if(!isMainThread2)
   {
     console.log("data listening");
-    dataServer.listen(inPort);
+    try{
+        dataServer.listen(inPort);
+    }
+    catch(err){
+      console.log("Data server has shut down");
+    }
   }
 }
 
@@ -340,7 +345,12 @@ let thriftServer = thrift.createServer(aInterface,{
 if(isMainThread)
 {
   console.log("Ctrl listening");
-  thriftServer.listen(9090);
+  try{
+      thriftServer.listen(9090);
+  }
+  catch(err){
+    console.log("Control server has shut down");
+  }
 }
 
 module.exports = {

### 2020-12-01 project/src/centralData/Clients/ControlClient.py
Both clients successfully integrated.

@@ -9,13 +9,6 @@ import time
 import math
 import threading
 
-class Control(object):
+class Control(ClientConnector):
     def __init__(self,IPAddr='127.0.0.1',port=9090):
-        self.DefaultPortNo = port
-        self.DefaultIp     = IPAddr
-    def Connect(ip=self.DefaultPortNo,port=self.DefauoltPortNo):
-        transport = TSocket.TSocket(ip,port)
-        transport = TTransport.TBufferedTransport(transport)
-        protocol  = TBinaryProtocol.TBinaryProtocol(transport)
-        client    = AgentInterface.Client(protocol)
-        return client,transport
+        super().__init__(AgentInterface,IPAddr,port)

### 2020-12-01 project/src/centralData/Clients/DataClient.py

@@ -9,13 +9,6 @@ import time
 import math
 import threading
 
-class Data(object):
+class Data(ClientConnector):
     def __init__(self,IPAddr='127.0.0.1',port=9091):
-        self.DefaultPortNo = port
-        self.DefaultIp     = IPAddr
-    def Connect(ip=self.DefaultPortNo,port=self.DefauoltPortNo):
-        transport = TSocket.TSocket(ip,port)
-        transport = TTransport.TBufferedTransport(transport)
-        protocol  = TBinaryProtocol.TBinaryProtocol(transport)
-        client    = AgentInterface.Client(protocol)
-        return client,transport
+        super().__init__(DataInterface,IPAddr,port)

### 2020-12-01 project/src/centralData/Clients/ThriftCommon.py

@@ -3,3 +3,34 @@ from thrift import Thrift
 from thrift.transport import TSocket
 from thrift.transport import TTransport
 from thrift.protocol import TBinaryProtocol
+
+class ClientConnector(object):
+    def __init__(self,
+                 ThriftInterface,
+                 IPAddr='127.0.0.1',
+                 port=9090):
+            self.DefaultPortNo = port
+            self.DefaultIp     = IPAddr
+            self.ThriftIFace   = ThriftInterface
+            self.Client        = None
+            self.Transport     = None
+    def Connect(self,ip=None,port=None):
+        if(ip==None):
+            ip=self.DefaultIp
+        if(port==None):
+            port=self.DefaultPortNo
+        transport = TSocket.TSocket(ip,port)
+        transport = TTransport.TBufferedTransport(transport)
+        protocol  = TBinaryProtocol.TBinaryProtocol(transport)
+        client    = self.ThriftIFace.Client(protocol)
+
+        self.Client    = client
+        self.Transport = transport
+        return client
+    def OpenCommunication(self):
+        if(self.Transport):
+            self.Transport.open()
+            return True
+        return False
+    def CloseCommunication(self):
+        self.Transport.close()

### 2020-12-01 project/src/centralData/example.py

@@ -9,8 +9,9 @@ TEST_NAME = "name"
 # while(results[1]==False):
 #     time.sleep(1)
 
-client,tx = Connect()
-tx.open()
+client = Clients.Control()
+client.Connect()
+client.OpenCommunication()
 
 token = client.GetTokenByName(TEST_NAME)
 

### 2020-12-01 project/src/server/gameCore/gameLoop.js

@@ -7,7 +7,7 @@ const {Worker,isMainThread,parentPort} = require("worker_threads");
 
 let thrift     = require("thrift");
 let aInterface = require("../../centralData/API/RemoteCtrl/nodejs/AgentInterface");
-let ttypes     = require("../../centralData/API/RemoteCtrl/nodejs/jstest_types");
+// let ttypes     = require("../../centralData/API/RemoteCtrl/nodejs/jstest_types");
 let dataInterface = require("../../centralData/API/Data/nodejs/DataInterface");
 
 let playerTanks = {}; //tracks all player tanks
@@ -241,10 +241,22 @@ function getSnapshotData() {
     return gameState;
 }
 
+var GetGameDataFunc = function(json){
+  console.log("GetGameData called");
+  return "Some other string";
+}
+var ExecuteTestsFunc = function(){
+  console.log("ExecuteTests called");
+}
+var GetTestResultsFunc = function(){
+  console.log("GetTestResults called");
+  return "Some string.";
+}
+
 dataServer = thrift.createServer(dataInterface,{
-  GetGameData: function(json){},
-  ExecuteTests: function(){},
-  GetTestRestults: function(){return "thisString";}
+  GetGameData:     GetGameDataFunc,
+  ExecuteTests:    ExecuteTestsFunc,
+  GetTestResults: GetTestResultsFunc
 });
 
 var GetTokenByNameFunc = function(name)
@@ -319,15 +331,19 @@ var GetPoseFunc = function(token)
 
 var StartDataServerFunc = function(inPort)
 {
-  const {Worker2,isMainThread2,parentPort2} = require("worker_threads");
-  if(!isMainThread2)
-  {
-    console.log("data listening");
-    try{
-        dataServer.listen(inPort);
-    }
-    catch(err){
-      console.log("Data server has shut down");
+  if(isMainThread){
+      const {Worker2,isMainThread2,parentPort2} = require("worker_threads");
+    if(!isMainThread2)
+    {
+      console.log("data listening");
+      console.log(inPort);
+      try{
+          dataServer.listen(inPort);
+          console.log("Data server has closed.")
+      }
+      catch(err){
+        console.log("Data server error has occurred.");
+      }
     }
   }
 }
@@ -347,9 +363,10 @@ if(isMainThread)
   console.log("Ctrl listening");
   try{
       thriftServer.listen(9090);
+      console.log("Control server has shut down.")
   }
   catch(err){
[…]

### 2020-12-01 project/src/centralData/bothExampleUsage.py
file delete, file rename

@@ -1,0 +1,13 @@
+import Clients
+
+ctrlClient = Clients.Control()
+ctrlClient.Connect()
+ctrlClient.OpenCommunication()
+token = ctrlClient.Client.GetTokenByName('name')
+print(token)
+
+ctrlClient.Client.StartDataServer(9091)
+
+dataClient = Clients.Data()
+dataClient.Connect(port=9091)
+dataClient.OpenCommunication()

### 2020-12-01 project/src/centralData/client.py

@@ -1,43 +1,0 @@
-from API.RemoteCtrl.python.PYAgentInterface import *
-import time
-import math
-import threading
-
-import thrift
-from thrift import Thrift
-from thrift.transport import TSocket
-from thrift.transport import TTransport
-from thrift.protocol import TBinaryProtocol
-
-def Connect(ip='127.0.0.1',port=9090):
-    transport = TSocket.TSocket(ip,port)
-    transport = TTransport.TBufferedTransport(transport)
-    protocol = TBinaryProtocol.TBinaryProtocol(transport)
-    client = AgentInterface.Client(protocol)
-    return client,transport
-
-
-def LoopConnect(state):
-    while(not state[0]):
-        try:
-            client,tx = Connect()
-            tx.open()
-            state[1] = True
-            print("Success...")
-            state[2],state[3] = client,tx
-            break
-        except Exception as ex:
-            pass
-        time.sleep(1)
-        print("trying again...")
-    print("Returning...")
-
-def TryConnect():
-    stopper = [False,False,None,None]
-    trd = threading.Thread(target=LoopConnect,args=(stopper,))
-    trd.start()
-    return stopper,trd
-
-if(__name__=='__main__'):
-    client,tx = Connect()
-    tx.open()

### 2020-12-01 project/src/centralData/API/Data/nodejs/DataInterface.js
Adding remote executable tests

@@ -114,6 +114,81 @@ DataInterface_GetGameData_result.prototype.write = function(output) {
   return;
 };
 
+var DataInterface_ExecuteTest_args = function(args) {
+  this.testNumber = null;
+  if (args) {
+    if (args.testNumber !== undefined && args.testNumber !== null) {
+      this.testNumber = args.testNumber;
+    }
+  }
+};
+DataInterface_ExecuteTest_args.prototype = {};
+DataInterface_ExecuteTest_args.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    var fid = ret.fid;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    switch (fid) {
+      case 1:
+      if (ftype == Thrift.Type.I32) {
+        this.testNumber = input.readI32();
+      } else {
+        input.skip(ftype);
+      }
+      break;
+      case 0:
+        input.skip(ftype);
+        break;
+      default:
+        input.skip(ftype);
+    }
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+DataInterface_ExecuteTest_args.prototype.write = function(output) {
+  output.writeStructBegin('DataInterface_ExecuteTest_args');
+  if (this.testNumber !== null && this.testNumber !== undefined) {
+    output.writeFieldBegin('testNumber', Thrift.Type.I32, 1);
+    output.writeI32(this.testNumber);
+    output.writeFieldEnd();
+  }
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
+var DataInterface_ExecuteTest_result = function(args) {
+};
+DataInterface_ExecuteTest_result.prototype = {};
+DataInterface_ExecuteTest_result.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    input.skip(ftype);
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+DataInterface_ExecuteTest_result.prototype.write = function(output) {
+  output.writeStructBegin('DataInterface_ExecuteTest_result');
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
 var DataInterface_ExecuteTests_args = function(args) {
 };
[…]

### 2020-12-01 project/src/centralData/API/Data/python/PYDataInterface/DataInterface.py

@@ -27,6 +27,14 @@ class Iface(object):
         """
         pass
 
+    def ExecuteTest(self, testNumber):
+        """
+        Parameters:
+         - testNumber
+
+        """
+        pass
+
     def ExecuteTests(self):
         pass
 
@@ -72,6 +80,36 @@ class Client(Iface):
         if result.success is not None:
             return result.success
         raise TApplicationException(TApplicationException.MISSING_RESULT, "GetGameData failed: unknown result")
+
+    def ExecuteTest(self, testNumber):
+        """
+        Parameters:
+         - testNumber
+
+        """
+        self.send_ExecuteTest(testNumber)
+        self.recv_ExecuteTest()
+
+    def send_ExecuteTest(self, testNumber):
+        self._oprot.writeMessageBegin('ExecuteTest', TMessageType.CALL, self._seqid)
+        args = ExecuteTest_args()
+        args.testNumber = testNumber
+        args.write(self._oprot)
+        self._oprot.writeMessageEnd()
+        self._oprot.trans.flush()
+
+    def recv_ExecuteTest(self):
+        iprot = self._iprot
+        (fname, mtype, rseqid) = iprot.readMessageBegin()
+        if mtype == TMessageType.EXCEPTION:
+            x = TApplicationException()
+            x.read(iprot)
+            iprot.readMessageEnd()
+            raise x
+        result = ExecuteTest_result()
+        result.read(iprot)
+        iprot.readMessageEnd()
+        return
 
     def ExecuteTests(self):
         self.send_ExecuteTests()
@@ -129,6 +167,7 @@ class Processor(Iface, TProcessor):
         self._handler = handler
         self._processMap = {}
         self._processMap["GetGameData"] = Processor.process_GetGameData
+        self._processMap["ExecuteTest"] = Processor.process_ExecuteTest
         self._processMap["ExecuteTests"] = Processor.process_ExecuteTests
         self._processMap["GetTestResults"] = Processor.process_GetTestResults
         self._on_message_begin = None
@@ -172,6 +211,29 @@ class Processor(Iface, TProcessor):
             msg_type = TMessageType.EXCEPTION
             result = TApplicationException(TApplicationException.INTERNAL_ERROR, 'Internal error')
         oprot.writeMessageBegin("GetGameData", msg_type, seqid)
+        result.write(oprot)
+        oprot.writeMessageEnd()
+        oprot.trans.flush()
+
+    def process_ExecuteTest(self, seqid, iprot, oprot):
[…]

### 2020-12-01 project/src/centralData/testingExample.py

@@ -1,0 +1,11 @@
+import Clients
+
+ctrlClient = Clients.Control()
+ctrlClient.Connect()
+ctrlClient.OpenCommunication()
+
+ctrlClient.Client.StartDataServer(9091)
+
+dataClient = Clients.Data()
+dataClient.Connect(port=9091)
+dataClient.OpenCommunication()

### 2020-12-01 project/src/client/src/testing/testingFramework.js

@@ -28,6 +28,8 @@ nodeTankTesting.prototype = {
     },
     createInstance: function(containerN, playerName) {
         let newSocket = io(this.socketURL);
+        console.log("***socket***");
+        console.log(this.socketURL);
         let newGame = new game(containerN, newSocket, this.tokens[this.tokens.length - 1], playerName);
         this.gameInstances.push(newGame);
 

### 2020-12-01 project/src/server/gameCore/gameLoop.js

@@ -245,8 +245,15 @@ var GetGameDataFunc = function(json){
   console.log("GetGameData called");
   return "Some other string";
 }
+var ExecuteTestFunc = function(testNumber){
+  console.log("ExecuteTests called");
+  let socketManager = require("./socket-manager");
+  socketManager.testingCall("RunTest",testNumber);
+}
 var ExecuteTestsFunc = function(){
   console.log("ExecuteTests called");
+  let socketManager = require("./socket-manager");
+  socketManager.testingCall("RunAllTests",{});
 }
 var GetTestResultsFunc = function(){
   console.log("GetTestResults called");
@@ -256,7 +263,8 @@ var GetTestResultsFunc = function(){
 dataServer = thrift.createServer(dataInterface,{
   GetGameData:     GetGameDataFunc,
   ExecuteTests:    ExecuteTestsFunc,
-  GetTestResults: GetTestResultsFunc
+  GetTestResults:  GetTestResultsFunc,
+  ExecuteTest:     ExecuteTestFunc
 });
 
 var GetTokenByNameFunc = function(name)
@@ -339,7 +347,7 @@ var StartDataServerFunc = function(inPort)
       console.log(inPort);
       try{
           dataServer.listen(inPort);
-          console.log("Data server has closed.")
+          // console.log("Data server has closed.")
       }
       catch(err){
         console.log("Data server error has occurred.");
@@ -363,7 +371,7 @@ if(isMainThread)
   console.log("Ctrl listening");
   try{
       thriftServer.listen(9090);
-      console.log("Control server has shut down.")
+      // console.log("Control server has shut down.")
   }
   catch(err){
     console.log("Control server error has occurred.");

### 2020-12-01 project/src/server/gameCore/socket-manager.js

@@ -84,9 +84,14 @@ function getImageData(){
   return imageData;
 }
 
+function TestingCall(eventName,args){
+  socket.emit(eventName,args);
+}
+
 module.exports = {
     setSocket: setSocket,
     broadcast: broadcast,
     flagSource: flagDataSource,
-    getImageData: getImageData
+    getImageData: getImageData,
+    testingCall: TestingCall
 };

### 2020-12-01 project/src/centralData/API/Data/nodejs/DataInterface.js
more testing updates

@@ -239,6 +239,56 @@ DataInterface_ExecuteTests_result.prototype.write = function(output) {
   return;
 };
 
+var DataInterface_RestartServer_args = function(args) {
+};
+DataInterface_RestartServer_args.prototype = {};
+DataInterface_RestartServer_args.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    input.skip(ftype);
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+DataInterface_RestartServer_args.prototype.write = function(output) {
+  output.writeStructBegin('DataInterface_RestartServer_args');
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
+var DataInterface_RestartServer_result = function(args) {
+};
+DataInterface_RestartServer_result.prototype = {};
+DataInterface_RestartServer_result.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    input.skip(ftype);
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+DataInterface_RestartServer_result.prototype.write = function(output) {
+  output.writeStructBegin('DataInterface_RestartServer_result');
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
 var DataInterface_GetTestResults_args = function(args) {
 };
 DataInterface_GetTestResults_args.prototype = {};
@@ -492,6 +542,59 @@ DataInterfaceClient.prototype.recv_ExecuteTests = function(input,mtype,rseqid) {
   callback(null);
 };
 
+DataInterfaceClient.prototype.RestartServer = function(callback) {
+  this._seqid = this.new_seqid();
+  if (callback === undefined) {
+    var _defer = Q.defer();
+    this._reqs[this.seqid()] = function(error, result) {
+      if (error) {
+        _defer.reject(error);
+      } else {
+        _defer.resolve(result);
+      }
+    };
+    this.send_RestartServer();
+    return _defer.promise;
+  } else {
+    this._reqs[this.seqid()] = callback;
+    this.send_RestartServer();
+  }
+};
+
[…]

### 2020-12-01 project/src/centralData/API/Data/python/PYDataInterface/DataInterface.py

@@ -38,6 +38,9 @@ class Iface(object):
     def ExecuteTests(self):
         pass
 
+    def RestartServer(self):
+        pass
+
     def GetTestResults(self):
         pass
 
@@ -135,6 +138,30 @@ class Client(Iface):
         iprot.readMessageEnd()
         return
 
+    def RestartServer(self):
+        self.send_RestartServer()
+        self.recv_RestartServer()
+
+    def send_RestartServer(self):
+        self._oprot.writeMessageBegin('RestartServer', TMessageType.CALL, self._seqid)
+        args = RestartServer_args()
+        args.write(self._oprot)
+        self._oprot.writeMessageEnd()
+        self._oprot.trans.flush()
+
+    def recv_RestartServer(self):
+        iprot = self._iprot
+        (fname, mtype, rseqid) = iprot.readMessageBegin()
+        if mtype == TMessageType.EXCEPTION:
+            x = TApplicationException()
+            x.read(iprot)
+            iprot.readMessageEnd()
+            raise x
+        result = RestartServer_result()
+        result.read(iprot)
+        iprot.readMessageEnd()
+        return
+
     def GetTestResults(self):
         self.send_GetTestResults()
         return self.recv_GetTestResults()
@@ -169,6 +196,7 @@ class Processor(Iface, TProcessor):
         self._processMap["GetGameData"] = Processor.process_GetGameData
         self._processMap["ExecuteTest"] = Processor.process_ExecuteTest
         self._processMap["ExecuteTests"] = Processor.process_ExecuteTests
+        self._processMap["RestartServer"] = Processor.process_RestartServer
         self._processMap["GetTestResults"] = Processor.process_GetTestResults
         self._on_message_begin = None
 
@@ -257,6 +285,29 @@ class Processor(Iface, TProcessor):
             msg_type = TMessageType.EXCEPTION
             result = TApplicationException(TApplicationException.INTERNAL_ERROR, 'Internal error')
         oprot.writeMessageBegin("ExecuteTests", msg_type, seqid)
+        result.write(oprot)
+        oprot.writeMessageEnd()
+        oprot.trans.flush()
+
+    def process_RestartServer(self, seqid, iprot, oprot):
+        args = RestartServer_args()
+        args.read(iprot)
+        iprot.readMessageEnd()
+        result = RestartServer_result()
+        try:
+            self._handler.RestartServer()
+            msg_type = TMessageType.REPLY
+        except TTransport.TTransportException:
+            raise
[…]

### 2020-12-01 project/src/centralData/Clients/ThriftCommon.py

@@ -4,6 +4,10 @@ from thrift.transport import TSocket
 from thrift.transport import TTransport
 from thrift.protocol import TBinaryProtocol
 
+import time
+TIMEOUT = 5
+#######################################
+#   Client base class:
 class ClientConnector(object):
     def __init__(self,
                  ThriftInterface,
@@ -33,4 +37,24 @@ class ClientConnector(object):
             return True
         return False
     def CloseCommunication(self):
-        self.Transport.close()
+        if(self.Transport):
+            self.Transport.close()
+    def AutoConnect(self):
+        t = time.time()
+        self.Connect()
+        while(True):
+            shouldRetry = time.time()-t < TIMEOUT
+            try:
+                self.OpenCommunication()
+                return
+            except Exception as exc:
+                if(not shouldRetry):
+                    return
+
+    def __enter__(self):
+        self.AutoConnect()
+        return self
+    def __exit__(self,excType,excValue,excTraceback):
+        time.sleep(.125)
+        self.CloseCommunication()
+#############################################

### 2020-12-01 project/src/centralData/testingExample.py

@@ -1,11 +1,24 @@
 import Clients
 
 ctrlClient = Clients.Control()
-ctrlClient.Connect()
-ctrlClient.OpenCommunication()
-
-ctrlClient.Client.StartDataServer(9091)
-
 dataClient = Clients.Data()
-dataClient.Connect(port=9091)
-dataClient.OpenCommunication()
+
+def ExecTests():
+    with ctrlClient as ctrl:
+        ctrl.Client.StartDataServer(9091)
+        with dataClient as dclient:
+            dclient.Client.ExecuteTests()
+
+def GetDataClient():
+    with ctrlClient as ctrl:
+        ctrl.Client.StartDataServer(9091)
+    dataClient.AutoConnect()
+
+# ctrlClient.Connect()
+# ctrlClient.OpenCommunication()
+#
+# ctrlClient.Client.StartDataServer(9091)
+#
+#
+# dataClient.Connect(port=9091)
+# dataClient.OpenCommunication()

### 2020-12-01 project/src/server/gameCore/gameLoop.js

@@ -257,14 +257,22 @@ var ExecuteTestsFunc = function(){
 }
 var GetTestResultsFunc = function(){
   console.log("GetTestResults called");
-  return "Some string.";
+  let socketManager = require("./socket-manager");
+  results = socketManager.getLastResults();
+  return results;
+}
+var RestartServerFunc = function(){
+  console.log("RestartServer called");
+  let socketManager = require("./socket-manager");
+  socketManager.testingCall("Restart",{});
 }
 
 dataServer = thrift.createServer(dataInterface,{
   GetGameData:     GetGameDataFunc,
   ExecuteTests:    ExecuteTestsFunc,
   GetTestResults:  GetTestResultsFunc,
-  ExecuteTest:     ExecuteTestFunc
+  ExecuteTest:     ExecuteTestFunc,
+  RestartServer:   RestartServerFunc
 });
 
 var GetTokenByNameFunc = function(name)

### 2020-12-01 project/src/server/gameCore/socket-manager.js

@@ -6,6 +6,8 @@ let socket = undefined;
 let broadcastChan = undefined;
 
 let imageData = "";
+let lastTestCheck = "";
+let resultsArrived = false;
 
 function setUpEvents() {
     if (socket !== undefined) {
@@ -52,6 +54,11 @@ function setUpEvents() {
             socket.on("screenShotSent", (data) => {
                 imageData = data;
             });
+
+            socket.on("TestResults",(data)=>{
+              lastTestCheck = data;
+              resultsArrived = true;
+            });
         });
     }
 }
@@ -88,10 +95,18 @@ function TestingCall(eventName,args){
   socket.emit(eventName,args);
 }
 
+function GetLastResults(){
+  resultsArrived = false;
+  socket.emit("GetResults");
+  while(resultsArrived===false){}
+  return lastTestCheck;
+}
+
 module.exports = {
     setSocket: setSocket,
     broadcast: broadcast,
     flagSource: flagDataSource,
     getImageData: getImageData,
-    testingCall: TestingCall
+    testingCall: TestingCall,
+    getLastResults: GetLastResults
 };

### 2020-12-01 project/src/centralData/Clients/DataClient.py
Remote testing and result collection works

@@ -9,6 +9,22 @@ import time
 import math
 import threading
 
+import json
+
+def TestAssist(results):
+    #dataClient.GetTestResults()
+    results = json.loads(results)
+    tests = [(ndx+1,x['pass'] if( x['pass'] or x['fail']) else None) for ndx,x in enumerate(results)]
+    return tests
+
 class Data(ClientConnector):
     def __init__(self,IPAddr='127.0.0.1',port=9091):
         super().__init__(DataInterface,IPAddr,port)
+    def GetTestResults(self):
+        if(self.Transport.isOpen()):
+            results = self.Client.GetTestResults()
+            if(len(results)==0):
+                print("Results: {}".format(results))
+                results = self.Client.GetTestResults()
+            return TestAssist(results)
+        return []

### 2020-12-01 project/src/centralData/Clients/ThriftCommon.py

@@ -5,6 +5,7 @@ from thrift.transport import TTransport
 from thrift.protocol import TBinaryProtocol
 
 import time
+
 TIMEOUT = 5
 #######################################
 #   Client base class:

### 2020-12-01 project/src/client/src/testing/testingFramework.js

@@ -28,8 +28,6 @@ nodeTankTesting.prototype = {
     },
     createInstance: function(containerN, playerName) {
         let newSocket = io(this.socketURL);
-        console.log("***socket***");
-        console.log(this.socketURL);
         let newGame = new game(containerN, newSocket, this.tokens[this.tokens.length - 1], playerName);
         this.gameInstances.push(newGame);
 

### 2020-12-01 project/src/server/gameCore/socket-manager.js

@@ -57,7 +57,6 @@ function setUpEvents() {
 
             socket.on("TestResults",(data)=>{
               lastTestCheck = data;
-              resultsArrived = true;
             });
         });
     }
@@ -98,7 +97,6 @@ function TestingCall(eventName,args){
 function GetLastResults(){
   resultsArrived = false;
   socket.emit("GetResults");
-  while(resultsArrived===false){}
   return lastTestCheck;
 }
 

### 2020-12-01 project/src/centralData/Clients/DataClient.py
Remote testing finished.

@@ -11,7 +11,7 @@ import threading
 
 import json
 
-def TestAssist(results):
+def TestResultAssist(results):
     #dataClient.GetTestResults()
     results = json.loads(results)
     tests = [(ndx+1,x['pass'] if( x['pass'] or x['fail']) else None) for ndx,x in enumerate(results)]
@@ -24,7 +24,10 @@ class Data(ClientConnector):
         if(self.Transport.isOpen()):
             results = self.Client.GetTestResults()
             if(len(results)==0):
-                print("Results: {}".format(results))
                 results = self.Client.GetTestResults()
-            return TestAssist(results)
+            return TestResultAssist(results)
         return []
+    def RunTests(self,n):
+        for i in range(n):
+            self.Client.ExecuteTest(i)
+            time.sleep(.5)

### 2020-12-01 project/src/server/gameCore/socket-manager.js

@@ -95,9 +95,10 @@ function TestingCall(eventName,args){
 }
 
 function GetLastResults(){
-  resultsArrived = false;
   socket.emit("GetResults");
-  return lastTestCheck;
+  result = lastTestCheck;
+  lastTestCheck = "";
+  return result;
 }
 
 module.exports = {

### 2020-12-02 project/src/centralData/API/Data/nodejs/DataInterface.js
adding example application

@@ -289,6 +289,81 @@ DataInterface_RestartServer_result.prototype.write = function(output) {
   return;
 };
 
+var DataInterface_GetTestCases_args = function(args) {
+};
+DataInterface_GetTestCases_args.prototype = {};
+DataInterface_GetTestCases_args.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    input.skip(ftype);
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+DataInterface_GetTestCases_args.prototype.write = function(output) {
+  output.writeStructBegin('DataInterface_GetTestCases_args');
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
+var DataInterface_GetTestCases_result = function(args) {
+  this.success = null;
+  if (args) {
+    if (args.success !== undefined && args.success !== null) {
+      this.success = args.success;
+    }
+  }
+};
+DataInterface_GetTestCases_result.prototype = {};
+DataInterface_GetTestCases_result.prototype.read = function(input) {
+  input.readStructBegin();
+  while (true) {
+    var ret = input.readFieldBegin();
+    var ftype = ret.ftype;
+    var fid = ret.fid;
+    if (ftype == Thrift.Type.STOP) {
+      break;
+    }
+    switch (fid) {
+      case 0:
+      if (ftype == Thrift.Type.STRING) {
+        this.success = input.readString();
+      } else {
+        input.skip(ftype);
+      }
+      break;
+      case 0:
+        input.skip(ftype);
+        break;
+      default:
+        input.skip(ftype);
+    }
+    input.readFieldEnd();
+  }
+  input.readStructEnd();
+  return;
+};
+
+DataInterface_GetTestCases_result.prototype.write = function(output) {
+  output.writeStructBegin('DataInterface_GetTestCases_result');
+  if (this.success !== null && this.success !== undefined) {
+    output.writeFieldBegin('success', Thrift.Type.STRING, 0);
+    output.writeString(this.success);
+    output.writeFieldEnd();
+  }
+  output.writeFieldStop();
+  output.writeStructEnd();
+  return;
+};
+
 var DataInterface_GetTestResults_args = function(args) {
 };
 DataInterface_GetTestResults_args.prototype = {};
[…]

### 2020-12-02 project/src/centralData/Clients/DataClient.py

@@ -31,3 +31,15 @@ class Data(ClientConnector):
         for i in range(n):
             self.Client.ExecuteTest(i)
             time.sleep(.5)
+    def GetTestCases(self):
+        prev = self.Client.GetTestCases()
+        time.sleep(.125)
+        t = time.time()
+        while(len(prev)==0 and time.time()-t < 5):
+            if(len(prev)>0):
+                break
+            prev = self.Client.GetTestCases()
+            time.sleep(.125)
+        if(len(prev)>0):
+            return [ x.strip().split('\n')[0] for x in json.loads(prev)]
+        return []

### 2020-12-02 project/src/centralData/testingExample.py

@@ -1,11 +1,19 @@
 import Clients
 
-ctrlClient = Clients.Control()
-dataClient = Clients.Data()
+from Preprocessing.imageProcessing import PreProcess,CVShow,DisplayStream
+
+ip = "173.255.226.26"
+localhost = '127.0.0.1'
+
+ip = localhost
+
+ctrlClient = Clients.Control(ip,9090)
+dataClient = Clients.Data(ip,9091)
+
 
 def ExecTests():
     with ctrlClient as ctrl:
-        ctrl.Client.StartDataServer(9091)
+        ctrl.Client.StartDataServer(9090)
         with dataClient as dclient:
             dclient.Client.ExecuteTests()
 
@@ -13,6 +21,17 @@ def GetDataClient():
     with ctrlClient as ctrl:
         ctrl.Client.StartDataServer(9091)
     dataClient.AutoConnect()
+
+images = []
+def ShowNow(xscale=1.0,yscale=1.0):
+    d = ctrlClient.Client.GetImageData(token)
+    while(len(d)==0):
+        d = ctrlClient.Client.GetImageData(token)
+        time.sleep(.1)
+    f = PreProcess(d,xscale,yscale)
+    print("shape: {}".format(f.shape))
+    images.append(f)
+    CVShow(f)
 
 # ctrlClient.Connect()
 # ctrlClient.OpenCommunication()

### 2020-12-02 project/src/demonstration/App/TestingFrame.py

@@ -1,0 +1,132 @@
+import sys
+sys.path.append("../centralData")
+from .utils import BrowserManager
+
+import Clients
+
+import wx
+import time
+
+gameDescriptor = "game"
+testDescriptor = "testing"
+
+hostedPage = "173.255.226.26"
+localhost  = '127.0.0.1'
+ip         = localhost
+
+ctrlClient = Clients.Control(ip,9090)
+dataClient = Clients.Data(ip,9091)
+
+def GetDataClient():
+    with ctrlClient as ctrl:
+        ctrl.Client.StartDataServer(9091)
+    dataClient.AutoConnect()
+
+def AddItem(text,panel,sizer):
+    temp = DispPanel(text,parent=panel)
+    sizer.Add(temp,0,wx.ALL,5)
+    return temp
+
+def Init():
+    browser = BrowserManager()
+    browser.AddBasePage('http://'+ip)
+    browser.AddSubPage(gameDescriptor,"")
+    browser.AddSubPage(testDescriptor,"unitTesting")
+    return browser
+
+
+class DispPanel(wx.Panel):
+    def __init__(self,name,*args,**kwargs):
+        wx.Panel.__init__(self,*args,**kwargs)
+        self.HorizontalSizer = wx.BoxSizer(wx.HORIZONTAL)
+        self.LabelT          = wx.StaticText(self,wx.ID_ANY,label="Test: ")
+        self.Text            = wx.StaticText(self,wx.ID_ANY,label=name,style=wx.BORDER_RAISED)
+        self.HorizontalSizer.Add(self.LabelT,0,wx.ALL,2)
+        self.HorizontalSizer.Add(self.Text,0,wx.ALL,2)
+        self.SetSizer(self.HorizontalSizer)
+
+    def GetValue(self):
+        return self.Text.GetValue()
+
+    def MarkFailed(self):
+        self.Text.SetBackgroundColour(wx.RED)
+    def MarkSucceeded(self):
+        self.Text.SetBackgroundColour(wx.GREEN)
+
+    def SetValue(self,v):
+        self.Text.SetLabel(str(v))
+
+class View(wx.Panel):
+    def __init__(self,*args,**kwargs):
+        wx.Panel.__init__(self,*args,**kwargs)
+        self.Horiz    = wx.BoxSizer(wx.VERTICAL)
+        self.Sz       = wx.BoxSizer(wx.VERTICAL)
+        self.BtnSizer = wx.BoxSizer(wx.HORIZONTAL)
+
[…]

### 2020-12-02 project/src/demonstration/App/exampleApplication.py

@@ -1,0 +1,21 @@
+from utils import BrowserManager
+import time
+
+website = 'http://173.255.226.26'
+port    = 8080
+
+game    = ""
+tests   = "unitTesting"
+
+gameDescriptor = "game"
+testDescriptor = "testing"
+
+browser = BrowserManager()
+
+browser.AddBasePage(website)
+browser.AddSubPage(gameDescriptor,game)
+browser.AddSubPage(testDescriptor,tests)
+
+browser.Load(gameDescriptor)
+time.sleep(3)
+browser.Load(testDescriptor)

### 2020-12-02 project/src/demonstration/App/utils.py

@@ -1,0 +1,25 @@
+import webbrowser
+
+class BrowserManager(object):
+    def __init__(self):
+        self.Browser = webbrowser.get()
+        self.BaseUrl = ""
+        self.Pages = {}
+        self.Port = 8080
+    def AddSubPage(self,name,urlPath):
+        self.Pages[name] = urlPath
+    def AddBasePage(self,page):
+        self.BaseUrl = page
+    def SetPort(self,port):
+        self.Port = port
+    def CleanPath(self,pathString):
+        return pathString.replace('\\','/')
+    def JoinPaths(self,pathA,pathB):
+        pathA = self.CleanPath(pathA).strip('/')
+        pathB = self.CleanPath(pathB).strip('/')
+        return pathA+'/'+pathB
+    def Load(self,pageName):
+        base = self.BaseUrl + ':' + str(self.Port)
+        path = self.JoinPaths(base,self.Pages[pageName])
+        if(not self.Browser.open(path)):
+            raise Exception("Could not load page: {}".format(path))

### 2020-12-02 project/src/demonstration/Main.py

@@ -1,0 +1,9 @@
+import wx
+import threading
+from App.TestingFrame import TestFrame
+
+app    = wx.App(False)
+window = TestFrame(None)
+
+window.Show()
+app.MainLoop()

### 2020-12-02 project/src/server/gameCore/gameLoop.js

@@ -266,13 +266,19 @@ var RestartServerFunc = function(){
   let socketManager = require("./socket-manager");
   socketManager.testingCall("Restart",{});
 }
+var GetCasesFunc = function(){
+  let socketManager = require("./socket-manager");
+  socketManager.testingCall("GetTestCases",{});
+  return socketManager.getCases();
+}
 
 dataServer = thrift.createServer(dataInterface,{
   GetGameData:     GetGameDataFunc,
   ExecuteTests:    ExecuteTestsFunc,
   GetTestResults:  GetTestResultsFunc,
   ExecuteTest:     ExecuteTestFunc,
-  RestartServer:   RestartServerFunc
+  RestartServer:   RestartServerFunc,
+  GetTestCases:        GetCasesFunc
 });
 
 var GetTokenByNameFunc = function(name)

### 2020-12-02 project/src/server/gameCore/socket-manager.js

@@ -8,6 +8,7 @@ let broadcastChan = undefined;
 let imageData = "";
 let lastTestCheck = "";
 let resultsArrived = false;
+let testCasesString = ""
 
 function setUpEvents() {
     if (socket !== undefined) {
@@ -58,6 +59,11 @@ function setUpEvents() {
             socket.on("TestResults",(data)=>{
               lastTestCheck = data;
             });
+
+            socket.on("TestCases",(data)=>{
+              console.log("TestCasses called");
+              testCasesString = data;
+            });
         });
     }
 }
@@ -94,6 +100,10 @@ function TestingCall(eventName,args){
   socket.emit(eventName,args);
 }
 
+function GetCases(){
+  return testCasesString;
+}
+
 function GetLastResults(){
   socket.emit("GetResults");
   result = lastTestCheck;
@@ -107,5 +117,6 @@ module.exports = {
     flagSource: flagDataSource,
     getImageData: getImageData,
     testingCall: TestingCall,
-    getLastResults: GetLastResults
+    getLastResults: GetLastResults,
+    getCases: GetCases
 };

### 2020-12-02 paper/PaperDraft2.tex
Updated paper

@@
 
-\title{Testing Methodologies for a Multiplayer Game Protocol\\
+\title{Testing Methodologies for Asynchronous Centralized Simulations\\
 }
@@
  to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.
-
-\section{Approach}
-Our approach is to develop a testing framework for NodeTank will combine abstract testing of models, unit testing, and functional testing into a single, yet modular, 
-utility. The effort of functional testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility 
-should be distributable just as the software being tested and a means of distributing and launching a test should be runnable from a single test location. Any data and 
-any results of a test run should also be collected and delivered to the single test location where it will be analyzed and classified as either a success or failure. 
-Current design will feature the integration of the Labstreaminglayer tool and a Labstreaminglayer server. This tool will allow for the collection of any data or output 
-deemed necessary for a given test. It will allow for record sub-millisecond timing of events from multiple machines over a local area network.
-
-For the goal of developing and testing the game locally on one machine, we will also be able to leverage the fact that it is built to run in the browser on
-an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated 
-system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
-its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect 
-the state of the simulation on each one of the said client machines independently. This would allow us to inspect the correctness of the model in real time from the 
-perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous 
-or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.
 
@@
 
+\section{Approach}
+Our approach is to develop a testing framework for NodeTank will combine abstract testing of models, unit testing, and functional testing into a single, yet modular, 
+utility. The effort of functional testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility 
+should be distributable just as the software being tested and a means of distributing and launching a test should be runnable from a single test location. Any data and 
+any results of a test run should also be collected and delivered to the single test location where it will be analyzed and classified as either a success or failure. 
+Current design will feature the integration of the Labstreaminglayer tool and a Labstreaminglayer server. This tool will allow for the collection of any data or output 
+deemed necessary for a given test. It will allow for record sub-millisecond timing of events from multiple machines over a local area network.
+
+For the goal of developing and testing the game locally on one machine, we will also be able to leverage the fact that it is built to run in the browser on
+an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated 
+system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
+its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect 
+the state of the simulation on each one of the said client machines independently. This would allow us to inspect the correctness of the model in real time from the 
+perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous 
+or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.
+
 \section{Implementation}
@@
 
+\subsection{Trained Model Approach}
+
+Discuss the setup for the trained model - the tools and automatic invocation
+
+\section{Case Study}
+
+Discuss the specificics of the game architecture here - show the actual code and frameworks
+
 \section{Conclusion}

### 2020-12-02 paper/PaperDraft2.tex
Added new reference

@@
 
-These are all concerns of NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
+These are all concerns of our case study, NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
  to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.
@@
 
-As this protocol will work with 3D graphical data, we need to present some prerequisite ideas that the reader may not be
-familiar with. Since the purpose of this paper is not to discuss how 3D graphics work, the explanation will be kept brief 
-as to only build up the necessary intuition.
+Before we may continue to discuss testing methodologies for centralized simulations, we should take a look at what exactly a centralized asynchronous simulation is. 
+In this section, we will take a look at the high-level overview of such a simulation before delving into the specific type of data utilized by NodeTank.
+
+\subsection{Architecture}
+
+In attempting to understand the
 
@@
 [3] R. Rezin, ”Model Checking in multiplayer games development”, Innopolis University, 
-2017, Available: https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=8432324
+2017, Available: https://arxiv.org/pdf/1712.01207.pdf
 
@@
  Available: https://ieeexplore.ieee.org/abstract/document/5361761
+
+[6] J. Smed, "Aspects of Networking in Multiplayer Computer Games", Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
+Available: https://www.researchgate.net/publication/269251176_Aspects_of_Networking_in_Multiplayer_Computer_Games
 \end{document}

### 2020-12-02 project/src/centralData/Clients/DataClient.py
more things

@@ -20,17 +20,20 @@ def TestResultAssist(results):
 class Data(ClientConnector):
     def __init__(self,IPAddr='127.0.0.1',port=9091):
         super().__init__(DataInterface,IPAddr,port)
+        self.Delay = .25
     def GetTestResults(self):
         if(self.Transport.isOpen()):
             results = self.Client.GetTestResults()
-            if(len(results)==0):
+            while(len(results)==0):
                 results = self.Client.GetTestResults()
             return TestResultAssist(results)
         return []
+    def SetDelay(self,delay):
+        self.Delay = delay
     def RunTests(self,n):
         for i in range(n):
             self.Client.ExecuteTest(i)
-            time.sleep(.5)
+            time.sleep(self.Delay)
     def GetTestCases(self):
         prev = self.Client.GetTestCases()
         time.sleep(.125)

### 2020-12-02 project/src/demonstration/App/TestingFrame.py

@@ -10,12 +10,10 @@ import time
 gameDescriptor = "game"
 testDescriptor = "testing"
 
-hostedPage = "173.255.226.26"
-localhost  = '127.0.0.1'
-ip         = localhost
+# ctrlClient = Clients.Control(ip,9090)
+# dataClient = Clients.Data(ip,9091)
 
-ctrlClient = Clients.Control(ip,9090)
-dataClient = Clients.Data(ip,9091)
+
 
 def GetDataClient():
     with ctrlClient as ctrl:
@@ -63,20 +61,29 @@ class View(wx.Panel):
         self.Sz       = wx.BoxSizer(wx.VERTICAL)
         self.BtnSizer = wx.BoxSizer(wx.HORIZONTAL)
 
+        self.servers = ["127.0.0.1","173.255.226.26"]
+        self.current = 0
+        self.ip      = self.servers[self.current]
+
         self.Panel    = wx.Panel(self,id=wx.ID_ANY,style=wx.BORDER_SUNKEN)
         self.BPanel   = wx.Panel(self,id=wx.ID_ANY)
 
-        self.button1  = wx.Button(self.BPanel,label='button1')
-        self.button2  = wx.Button(self.BPanel,label='button2')
+        self.textDisp = wx.StaticText(self.BPanel,wx.ID_ANY,label="Using: "+self.ip)
+        self.button1  = wx.Button(self.BPanel,label='ToggleServer')
+        self.button2  = wx.Button(self.BPanel,label='CheckTests')
         self.button3  = wx.Button(self.BPanel,label='PopulateTests')
+        self.button4  = wx.Button(self.BPanel,label='RunTests')
 
-        self.button1.Bind(wx.EVT_BUTTON,self.OnAdd)
+        self.button1.Bind(wx.EVT_BUTTON,self.Toggle)
         self.button2.Bind(wx.EVT_BUTTON,self.OnSecond)
-        self.button3.Bind(wx.EVT_BUTTON,self.OnThird)
+        self.button4.Bind(wx.EVT_BUTTON,self.OnRun)
+        self.button3.Bind(wx.EVT_BUTTON,self.OnCheckTests)
 
         self.BtnSizer.Add(self.button1,0,wx.ALL,5)
         self.BtnSizer.Add(self.button2,0,wx.ALL,5)
+        self.BtnSizer.Add(self.button4,0,wx.ALL,5)
[…]

### 2020-12-02 project/src/server/gameCore/gameLoop.js

@@ -263,8 +263,8 @@ var GetTestResultsFunc = function(){
 }
 var RestartServerFunc = function(){
   console.log("RestartServer called");
-  let socketManager = require("./socket-manager");
-  socketManager.testingCall("Restart",{});
+  let gstate = require("./global-state");
+  gstate.setResetServer(true);
 }
 var GetCasesFunc = function(){
   let socketManager = require("./socket-manager");

### 2020-12-03 project/src/demonstration/App/TestingFrame.py
another change

@@ -98,11 +98,13 @@ class View(wx.Panel):
         self.SetEnabledButton(3)
         self.button1.Enable()
 
-    def RemoveIt(self):
+    def ClearPanel(self):
         for item in self.Disps:
             item.Destroy()
         self.Disps = []
         self.Horiz.Layout()
+        self.GetParent()._Resize()
+
     def SetEnabledButton(self,*btns):
         buttons = [self.button1,self.button2,self.button4,self.button3]
         for button in buttons:
@@ -127,7 +129,7 @@ class View(wx.Panel):
         self.current = self.current%2
         self.ip = self.servers[self.current]
         self.textDisp.SetLabel("Using: "+self.ip)
-        self.RemoveIt()
+        self.ClearPanel()
 
     def OnRun(self,event):
         self.SetEnabledButton(-1)
@@ -147,10 +149,13 @@ class View(wx.Panel):
         self.SetEnabledButton(0,3)
 
     def OnCheckTests(self,event):
+        print("size: {}".format(self.Horiz.GetSize()))
+        self.ClearPanel()
         self.SetEnabledButton(-1)
         self.LoadTestThings()
         self.browser.Load(testDescriptor)
         time.sleep(2)
+        print("size: {}".format(self.Horiz.GetSize()))
 
         with self.ctrlClient as ctrl:
             ctrl.Client.StartDataServer(9091)
@@ -172,5 +177,7 @@ class TestFrame(wx.Frame):
         wx.Frame.__init__(self,*args,**kwargs)
         self.Panel = View(self,
                           id  =wx.ID_ANY,
-                          size=(300,300),
+                          size=(550,550),
                           pos =(50,50))
+    def _Resize(self):
+        self.SetSize(self.Panel.GetSize())

### 2020-12-03 paper/PaperDraft2.tex
Paper Update

@@
 
-In attempting to understand the
+In attempting to understand the architecture of a centralized simulation, we must also understand under which cirmucstances such an architecture is desired. For example,
+let's assume that we have some data that we would like to share between one or more clients, with a client being a receiver which is interested in some data. At a very high level, such
+a data sharing layout can be split into two categories: peer-peer and client-server. Smed et. al[6] describes the different layouts in detail, however, generally a peer-peer architecture 
+is defined as having two or more clients which have all, or part of some data which is then shared equally each peer. In this scenario, each client is equal to every other client, and thus,
+would have to be fully connected to one another[6]. This type of architecture has its own advantages when it comes to certain types of systems, such as file sharing and lock-step simulations,
+however we cannot maintain the type of centralized simulation which is pertinent to our topic.
 

### 2020-12-03 paper/PaperDraft2.tex
Added new figure
Paper update

@@
 
-\subsection{Architecture}
+\subsection{Network Architecture}
 
@@
 a data sharing layout can be split into two categories: peer-peer and client-server. Smed et. al[6] describes the different layouts in detail, however, generally a peer-peer architecture 
-is defined as having two or more clients which have all, or part of some data which is then shared equally each peer. In this scenario, each client is equal to every other client, and thus,
+is defined as having two or more clients which have all, or part of some data which is then shared equally each peer(Fig. 1). In this scenario, each client is equal to every other client, and thus,
 would have to be fully connected to one another[6]. This type of architecture has its own advantages when it comes to certain types of systems, such as file sharing and lock-step simulations,
 however we cannot maintain the type of centralized simulation which is pertinent to our topic.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 5cm] {NetworkArchitecture.jpg}}
+\caption{Example of a peer to peer and client server architecture}
+\end{figure}
+
+Another type of network architecture exists which has one server serve multiple clients, client-server(Fig. 1). In this type of architecture, one node is designated as the server,
+and all authoritative communication is handled through it before being sent to the clients[6]. As noted in Fig 1, we can see that any number of clients may connect to the server
+at any one time, and clients do not have to be fully connected since the server is the authoritative source. The client-server architecture will be the target of our testing methodologies
+and framework. Although peer-peer has its own valid use cases, it is not appropriate for a centralized simulation and would likewise necessitate a different approach to testing.
 
@@
 
-[6] J. Smed, "Aspects of Networking in Multiplayer Computer Games", Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
+[6] J. Smed, “Aspects of Networking in Multiplayer Computer Games“, Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
 Available: https://www.researchgate.net/publication/269251176_Aspects_of_Networking_in_Multiplayer_Computer_Games

### 2020-12-03 paper/PaperDraft2.tex
Another paper update

@@
 \section{Introduction}
-In our work we aim to create a testing framework for an online multiplayer javascript application called NodeTank. This application involves two primary components, 
-a server, and one or more connected clients. Each client instance renders the play environment to the players as well as a tank object and accepts control inputs from 
+In our work we aim to create a testing framework for centralized simulations serving one or more clients concurrently. In order to accomplish the goal of serving
+multiple clients concurrently and in a timely manner, the server must communicate with the clients in an asynchronous manner in that there can be no reliance 
+on confirming whether a data packet was received successfully, the server simply broadcasts any updates to the simulation state to all clients. With these considerations
+in mind, any rigorous and complete testing must account for these features. We will be introducing a number of different approaches with which to build a complete, end to end
+testing framework which can be used to ensure the correctness and completeness of any system utilizing a centralized simulation.
+
+Unit testing can be achieved through traditional means of subjecting applicable functions to predetermined inputs and comparing their results to expected results. 
+Functional testing presents a less straight-forward solution. For example, instead of treating testing in the traditional sense of invoking one method at a time,
+we can designate a certain action within the game to be the target of functional testing. Taking it one step further, we have the end-goal of automating such a process such that 
+it can be invoked with little operator input, akin to how a set of unit tests would function. In order to acomplish the task of automation, we will provide solutions to the problem
+of asynchronicity.
+
+In the latter half of the paper, we will be introducing an actual instance of such a simulation, a browser-based online multiplayer javascript application called NodeTank. 
+This application involves two primary components, a server, and one or more connected clients.
+Each client instance renders the game environment to the players as well as a tank object which accepts control inputs from
 a player. Client instances are responsible for forwarding control inputs to the server. The server is responsible for tracking and maintaining state information relevant 
@@
 with minimal latency in order to provide a continuous stream of snapshots of the game’s state. Client applications are also responsible for recreating and displaying this 
-information for the player with the end-goal of providing all players with consistent up-to-date information.
-
-Unit testing can be achieved through traditional means of subjecting applicable functions to predetermined inputs and comparing their results to expected results. 
-Functional testing presents a less straight-forward solution. In the basic case, there are two clients and one server, three separate processes that are interacting 
-with one another. These interactions can potentially generate a very wide range of outputs and behaviors of which only a very small subset would be 
-considered correct. Not only do the specific actions and reactions between these processes determine program correctness, but the timing between them determine correctness.
+information for the player with the end-goal of providing all players with consistent up-to-date information. We will apply the framework concepts developed in the former sections to this 
+case study to demonstrate its efficacy.
 

### 2020-12-03 paper/PaperDraft2.tex
Remote Testing, some additional outlining

--- 2020-12-03 paper/PaperDraft2.tex
@@
 
-\title{Testing Methodologies for Asynchronous Centralized Simulations\\
+\title{Testing Methodologies for a Multiplayer Game Protocol\\
 }
@@
 
-These are all concerns of our case study, NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
+These are all concerns of NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
  to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.
+
+\section{Approach}
+Our approach is to develop a testing framework for NodeTank will combine abstract testing of models, unit testing, and functional testing into a single, yet modular,
+utility. The effort of functional testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility
+should be distributable just as the software being tested and a means of distributing and launching a test should be runnable from a single test location. Any data and
+any results of a test run should also be collected and delivered to the single test location where it will be analyzed and classified as either a success or failure.
+Current design will feature the integration of the Labstreaminglayer tool and a Labstreaminglayer server. This tool will allow for the collection of any data or output
+deemed necessary for a given test. It will allow for record sub-millisecond timing of events from multiple machines over a local area network.
+
+For the goal of developing and testing the game locally on one machine, we will also be able to leverage the fact that it is built to run in the browser on
+an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated
+system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
+its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect
+the state of the simulation on each one of the said client machines independently. This would allow us to inspect the correctness of the model in real time from the
+perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous
+or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.
 
@@
 
-Before we may continue to discuss testing methodologies for centralized simulations, we should take a look at what exactly a centralized asynchronous simulation is. 
-In this section, we will take a look at the high-level overview of such a simulation before delving into the specific type of data utilized by NodeTank.
-
-\subsection{Architecture}
-
-In attempting to understand the architecture of a centralized simulation, we must also understand under which cirmucstances such an architecture is desired. For example,
-let's assume that we have some data that we would like to share between one or more clients, with a client being a receiver which is interested in some data. At a very high level, such
-a data sharing layout can be split into two categories: peer-peer and client-server. Smed et. al[6] describes the different layouts in detail, however, generally a peer-peer architecture 
-is defined as having two or more clients which have all, or part of some data which is then shared equally each peer. In this scenario, each client is equal to every other client, and thus,
-would have to be fully connected to one another[6]. This type of architecture has its own advantages when it comes to certain types of systems, such as file sharing and lock-step simulations,
-however we cannot maintain the type of centralized simulation which is pertinent to our topic.
+As this protocol will work with 3D graphical data, we need to present some prerequisite ideas that the reader may not be
+familiar with. Since the purpose of this paper is not to discuss how 3D graphics work, the explanation will be kept brief
+as to only build up the necessary intuition.
 
@@
 
-\section{Approach}
-Our approach is to develop a testing framework for NodeTank will combine abstract testing of models, unit testing, and functional testing into a single, yet modular, 
-utility. The effort of functional testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility 
-should be distributable just as the software being tested and a means of distributing and launching a test should be runnable from a single test location. Any data and 
-any results of a test run should also be collected and delivered to the single test location where it will be analyzed and classified as either a success or failure. 
-Current design will feature the integration of the Labstreaminglayer tool and a Labstreaminglayer server. This tool will allow for the collection of any data or output 
-deemed necessary for a given test. It will allow for record sub-millisecond timing of events from multiple machines over a local area network.
-
-For the goal of developing and testing the game locally on one machine, we will also be able to leverage the fact that it is built to run in the browser on
-an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated 
-system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
-its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect 
-the state of the simulation on each one of the said client machines independently. This would allow us to inspect the correctness of the model in real time from the 
-perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous 
-or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.
-
 \section{Implementation}
@@
 
-\subsection{Trained Model Approach}
+\subsection{Remote Testing}
 
-Discuss the setup for the trained model - the tools and automatic invocation
+\subsubsection{Core RPC Services}Remote testing of the target application is achieved through an adaptable and extensible pair of RPC services.
+Two APIs, 'Data' and 'RemoteCtrl', that enable remote testing and they are capable of being updated and expanded quite easily as the application's range of behaviors grow during its lifetime.
+Each API service is defined in an IDL(Interface Description Language) file.
+Each defines the a service's name followed by generic a list call signatures of the functions that shoould be exposed by the service.
+The IDL offers several plain data types such booleans, floating points, a string type, and signed integers of the typical varying bit-widths.
+Basic C-style structures and enumerations may also be defined to add versatility to the services defined types.
+\subsubsection{RPC Adaptability}As the application grows and new types of interactions and information need to be handled, the same pair of IDL need only minor editing by the maintainer.
+Automatic generations scripts may be rerun at each stage of changing demand.
+The resulting output is a fully-formed supporting library in the target programming language of choice for, both, the client and server sides of each RPC service.
+The RPC-server half of each API is included and/or linked to from the simulation's server to allow both services awareness of and access to all necessary data of the simulation's clients.
+In the event of new or changing data types, the client simulation needs only to be rebuilt in the case of a compiled-language and no changes are required for interpreted languages.
+In the case of new or changing functions, the auto-generated RPC handlers need only be given function bodies by the tester.
+Building remote testing utilities for the simulation is easily done thanks to this process, as there are no dependencies between the programming language of the simulation's server and the RPC client.
+The RPC service itself manages all translation between native data types of the server and it's RPC client.
+This means the RPC service manages the serialization/deserialization and transport of all function arguments and return values, byte-order translation between differing host hardware, and member alignment between differing host operating environments.
+All these features allow for a simulation written in javascript, C++, Java, Python, C\#, etc.
+to agnostically cooperate with any client written in any other supported language and host operating environemnt.
+\subsubsection{Distributibility}With an underlying TCP or UDP transport layer, this remote testing strategy allows for a wide range of geographical testing configurations to be thuroughly explored.
+Testing and examination of the system may be performed in a close-proximity LAN configuration, or the simulation server and its clients may be much more georgraphically separated, communicating over the Internet with one another and the testing client itself.
 
 \section{Case Study}
-
-Discuss the specificics of the game architecture here - show the actual code and frameworks
+\subsection{Remote RPC Services}
+\subsubsection{Remote Testing Service}
+\paragraph{Hooks into the javascript testing framework}
+\subsubsection{Remote Control Service}
+\paragraph{Injecting user input}
+\paragraph{Extracting the rendered environment}
 
 \section{Conclusion}
+\subsection{Future Work}
 
@@
 [1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016,
-Available from ProQuest Dissertations & Theses Global. (1881527059). 
+Available from ProQuest Dissertations \& Theses Global. (1881527059).
 Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924
@@
 [3] R. Rezin, ”Model Checking in multiplayer games development”, Innopolis University,
-2017, Available: https://arxiv.org/pdf/1712.01207.pdf
+2017, Available: https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=8432324
 
@@
  Available: https://ieeexplore.ieee.org/abstract/document/5361761
-
-[6] J. Smed, "Aspects of Networking in Multiplayer Computer Games", Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
-Available: https://www.researchgate.net/publication/269251176_Aspects_of_Networking_in_Multiplayer_Computer_Games
 \end{document}

### 2020-12-03 paper/PaperDraft2.tex

@@
 \section{Introduction}
-In our work we aim to create a testing framework for an online multiplayer javascript application called NodeTank. This application involves two primary components,
-a server, and one or more connected clients. Each client instance renders the play environment to the players as well as a tank object and accepts control inputs from
+In our work we aim to create a testing framework for centralized simulations serving one or more clients concurrently. In order to accomplish the goal of serving
+multiple clients concurrently and in a timely manner, the server must communicate with the clients in an asynchronous manner in that there can be no reliance
+on confirming whether a data packet was received successfully, the server simply broadcasts any updates to the simulation state to all clients. With these considerations
+in mind, any rigorous and complete testing must account for these features. We will be introducing a number of different approaches with which to build a complete, end to end
+testing framework which can be used to ensure the correctness and completeness of any system utilizing a centralized simulation.
+
+Unit testing can be achieved through traditional means of subjecting applicable functions to predetermined inputs and comparing their results to expected results.
+Functional testing presents a less straight-forward solution. For example, instead of treating testing in the traditional sense of invoking one method at a time,
+we can designate a certain action within the game to be the target of functional testing. Taking it one step further, we have the end-goal of automating such a process such that
+it can be invoked with little operator input, akin to how a set of unit tests would function. In order to acomplish the task of automation, we will provide solutions to the problem
+of asynchronicity.
+
+In the latter half of the paper, we will be introducing an actual instance of such a simulation, a browser-based online multiplayer javascript application called NodeTank.
+This application involves two primary components, a server, and one or more connected clients.
+Each client instance renders the game environment to the players as well as a tank object which accepts control inputs from
 a player. Client instances are responsible for forwarding control inputs to the server. The server is responsible for tracking and maintaining state information relevant
@@
 with minimal latency in order to provide a continuous stream of snapshots of the game’s state. Client applications are also responsible for recreating and displaying this
-information for the player with the end-goal of providing all players with consistent up-to-date information.
-
-Unit testing can be achieved through traditional means of subjecting applicable functions to predetermined inputs and comparing their results to expected results.
-Functional testing presents a less straight-forward solution. In the basic case, there are two clients and one server, three separate processes that are interacting
-with one another. These interactions can potentially generate a very wide range of outputs and behaviors of which only a very small subset would be
-considered correct. Not only do the specific actions and reactions between these processes determine program correctness, but the timing between them determine correctness.
+information for the player with the end-goal of providing all players with consistent up-to-date information. We will apply the framework concepts developed in the former sections to this
+case study to demonstrate its efficacy.
 
@@
 
-For the goal of developing and testing the game locally on one machine, we will also be able to leverage the fact that it is built to run in the browser on
-an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated
-system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
-its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect
-the state of the simulation on each one of the said client machines independently. This would allow us to inspect the correctness of the model in real time from the
-perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous
-or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.
+\subsection{Network Architecture}
 
-\section{Background}
+In attempting to understand the architecture of a centralized simulation, we must also understand under which cirmucstances such an architecture is desired. For example,
+let's assume that we have some data that we would like to share between one or more clients, with a client being a receiver which is interested in some data. At a very high level, such
+a data sharing layout can be split into two categories: peer-peer and client-server. Smed et. al[6] describes the different layouts in detail, however, generally a peer-peer architecture
+is defined as having two or more clients which have all, or part of some data which is then shared equally each peer(Fig. 1). In this scenario, each client is equal to every other client, and thus,
+would have to be fully connected to one another[6]. This type of architecture has its own advantages when it comes to certain types of systems, such as file sharing and lock-step simulations,
+however we cannot maintain the type of centralized simulation which is pertinent to our topic.
 
-As this protocol will work with 3D graphical data, we need to present some prerequisite ideas that the reader may not be
-familiar with. Since the purpose of this paper is not to discuss how 3D graphics work, the explanation will be kept brief
-as to only build up the necessary intuition.
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 5cm] {NetworkArchitecture.jpg}}
+\caption{Example of a peer to peer and client server architecture}
+\end{figure}
+
+Another type of network architecture exists which has one server serve multiple clients, client-server(Fig. 1). In this type of architecture, one node is designated as the server,
+and all authoritative communication is handled through it before being sent to the clients[6]. As noted in Fig 1, we can see that any number of clients may connect to the server
+at any one time, and clients do not have to be fully connected since the server is the authoritative source. The client-server architecture will be the target of our testing methodologies
+and framework. Although peer-peer has its own valid use cases, it is not appropriate for a centralized simulation and would likewise necessitate a different approach to testing.
 
@@
  Available: https://ieeexplore.ieee.org/abstract/document/5361761
+
+[6] J. Smed, “Aspects of Networking in Multiplayer Computer Games“, Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
+Available: https://www.researchgate.net/publication/269251176\_Aspects\_of\_Networking\_in\_Multiplayer\_Computer\_Games
 \end{document}

### 2020-12-03 paper/PaperDraft2.tex
Adding more, bookmarking this

@@
 \subsection{Remote RPC Services}
+Our implementation of the \textit{Data} and \textit{RemoteCtrl} APIs were built upon a tool known as Thrift, originally created by Facebook, but now managed by Apache.
+The RPC services contain several functions, between the two of them, for retrieving and executing testing and control operations including \textit{GetTokenByName}, \textit{GetPose}, \textit{SetMove}, \textit{Fire}, \textit{StartDataServer}, \textit{ExecuteTest}, \textit{GetTestResults}, and \textit{GetTestCases} to name a few.
+The RPC handlers of each RPC services are setup within \textit{gameCore}, the game's primary server.
+From here, they are pointed to the appropriate handling functions.
+These handlers allow for the computational logic of the services to access all the necessary information from \textit{gameLoop.js}, \textit{global-state.js}, and \textit{socket-manager.js}.
+
 \subsubsection{Remote Testing Service}
-\paragraph{Hooks into the javascript testing framework}
+Within \textit{gameCore} the RPC host objects are setup each to operate within their own thread, alongside the game's primary servers.
 \subsubsection{Remote Control Service}
@@
 \paragraph{Extracting the rendered environment}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 5cm, height = 6cm] {images/remoteTesting.PNG}}
+\caption{Example of a testing application built using our remote testing APIs.
+This instance can cycle between multiple remote simulation servers.
+It populates a list of available unit tests available on that server, can execute them, and then presents the results to the tester by highlighting list items in green or red to indicate pass or fail respectively.}
+\end{figure}
 

### 2020-12-03 paper/PaperDraft2.tex
Paper Update

--- 2020-12-03 paper/PaperDraft2.tex
@@
 
-These are all concerns of NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
+These are all concerns of our case study, NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
  to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.
 
-\section{Approach}
-Our approach is to develop a testing framework for NodeTank will combine abstract testing of models, unit testing, and functional testing into a single, yet modular,
-utility. The effort of functional testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility
-should be distributable just as the software being tested and a means of distributing and launching a test should be runnable from a single test location. Any data and
-any results of a test run should also be collected and delivered to the single test location where it will be analyzed and classified as either a success or failure.
-Current design will feature the integration of the Labstreaminglayer tool and a Labstreaminglayer server. This tool will allow for the collection of any data or output
-deemed necessary for a given test. It will allow for record sub-millisecond timing of events from multiple machines over a local area network.
+\section{Background}
+
+Before we may continue to discuss testing methodologies for centralized simulations, we should take a look at what exactly a centralized asynchronous simulation is. 
+In this section, we will take a look at the high-level overview of such a simulation before delving into the specific type of data utilized by NodeTank.
 
@@
 \centerline{\includegraphics [width = 9cm, height = 5cm] {NetworkArchitecture.jpg}}
-\caption{Example of a peer to peer and client server architecture}
+\caption{Example of a Client-Server and Peer-Peer Architecture}
 \end{figure}
@@
 at any one time, and clients do not have to be fully connected since the server is the authoritative source. The client-server architecture will be the target of our testing methodologies
-and framework. Although peer-peer has its own valid use cases, it is not appropriate for a centralized simulation and would likewise necessitate a different approach to testing.
+and framework. Although peer-peer has its own valid use cases, it is not appropriate for a centralized simulation and would likewise necessitate a different approach to testing, and thus,
+the remainder of this paper will serve a client-server architecture.
+
+With the type of architecture selected, the only remaining task is to introduce the mechanism by which one node communicates with another node. For example, we must answer
+the question of how Client 1 and send and receive information from Client 4. Clearly, given that we need to have a centralized simulation, that information must pass through 
+the server. The only remaining question is how the server is not only connected to each client, but when that information is to be relayed. There are generally two methods of transmitting
+data to and from clients: unicast or broadcast[6]. Fig. 2 demonstrates a high-level overview of the two transmission types.
+
+The main distinction being that unicast allows one node to initate and send some data to a different node while broadcast allows a node to send information to all other nodes at the same time. 
+Intuitively, this implies that an unicast approach would have to initiate and conduct as many transactions as there are nodes.
+Naturally, this does not happen simultaneously and given sufficient nodes,
+the probability that the simulation comes out of sync between clients increases. Therefore, since there is only one true simulation in the system, it becomes advantageous to leverage the ability of 
+to broadcast a message simultaneously to all other nodes.
+The advantage of on-time dispatching of data becomes ever more noticeable when dealing with the type of software we will discuss in the case study, multiplayer
+games.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 5cm] {TransmissionArchitecture.jpg}}
+\caption{Example of Unicast and Broadcast Transmission Architecture}
+\end{figure}
 
@@
 
+\section{Approach}
+Our approach is to develop a testing framework for NodeTank will combine abstract testing of models, unit testing, and functional testing into a single, yet modular, 
+utility. The effort of functional testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility 
+should be distributable just as the software being tested and a means of distributing and launching a test should be runnable from a single test location. Any data and 
+any results of a test run should also be collected and delivered to the single test location where it will be analyzed and classified as either a success or failure. 
+Current design will feature the integration of the Labstreaminglayer tool and a Labstreaminglayer server. This tool will allow for the collection of any data or output 
+deemed necessary for a given test. It will allow for record sub-millisecond timing of events from multiple machines over a local area network.
+
+For the goal of developing and testing the game locally on one machine, we will also be able to leverage the fact that it is built to run in the browser on
+an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated 
+system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
+its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect 
+the state of the simulation on each one of the said client machines independently. This would allow us to inspect the correctness of the model in real time from the 
+perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous 
+or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.
+
 \section{Implementation}
-
-With the all of the prerequisite work complete, the implementation of the the game and protocol will be discussed. For reference,
-the project code is located at (https://github.com/spac3nerd/CSI-5390Proj). The nodejs server
-will need to run both traditional HTTP transactons and socket transactions. The HTTP transactions are used to ask the server if
-there are any open spots in the game, and whether access is granted to a new player. If access is granted, then the server will return
-an unique token to the client with which a socket connection can be requested. The client then requests entry into the game
-with the token and a tunnel is established between the client and the server.
-
-In the following sections we will cover the specific testing implementations with the goal of addressing the problem of rigorously testing NodeTank, or any
-other multiplayer game built on the NodeJS platform.
 
@@
 
-\subsection{Remote Testing}
+\subsection{Trained Model Approach}
 
-\subsubsection{Core RPC Services}Remote testing of the target application is achieved through an adaptable and extensible pair of RPC services.
-Two APIs, 'Data' and 'RemoteCtrl', that enable remote testing and they are capable of being updated and expanded quite easily as the application's range of behaviors grow during its lifetime.
-Each API service is defined in an IDL(Interface Description Language) file.
-Each defines the a service's name followed by generic a list call signatures of the functions that shoould be exposed by the service.
-The IDL offers several plain data types such booleans, floating points, a string type, and signed integers of the typical varying bit-widths.
-Basic C-style structures and enumerations may also be defined to add versatility to the services defined types.
-\subsubsection{RPC Adaptability}As the application grows and new types of interactions and information need to be handled, the same pair of IDL need only minor editing by the maintainer.
-Automatic generations scripts may be rerun at each stage of changing demand.
-The resulting output is a fully-formed supporting library in the target programming language of choice for, both, the client and server sides of each RPC service.
-The RPC-server half of each API is included and/or linked to from the simulation's server to allow both services awareness of and access to all necessary data of the simulation's clients.
-In the event of new or changing data types, the client simulation needs only to be rebuilt in the case of a compiled-language and no changes are required for interpreted languages.
-In the case of new or changing functions, the auto-generated RPC handlers need only be given function bodies by the tester.
-Building remote testing utilities for the simulation is easily done thanks to this process, as there are no dependencies between the programming language of the simulation's server and the RPC client.
-The RPC service itself manages all translation between native data types of the server and it's RPC client.
-This means the RPC service manages the serialization/deserialization and transport of all function arguments and return values, byte-order translation between differing host hardware, and member alignment between differing host operating environments.
-All these features allow for a simulation written in javascript, C++, Java, Python, C\#, etc.
-to agnostically cooperate with any client written in any other supported language and host operating environemnt.
-\subsubsection{Distributibility}With an underlying TCP or UDP transport layer, this remote testing strategy allows for a wide range of geographical testing configurations to be thuroughly explored.
-Testing and examination of the system may be performed in a close-proximity LAN configuration, or the simulation server and its clients may be much more georgraphically separated, communicating over the Internet with one another and the testing client itself.
+Discuss the setup for the trained model - the tools and automatic invocation
 
 \section{Case Study}
-\subsection{Remote RPC Services}
-\subsubsection{Remote Testing Service}
-\paragraph{Hooks into the javascript testing framework}
-\subsubsection{Remote Control Service}
-\paragraph{Injecting user input}
-\paragraph{Extracting the rendered environment}
+
+With the all of the prerequisite work complete, the implementation of the testing framework for the game and protocol will be discussed. For reference,
+the project code is located at (https://github.com/spac3nerd/CSI-5390Proj). The NodeJS server 
+will need to run both traditional HTTP transactons and socket transactions. The HTTP transactions are used to ask the server if 
+there are any open spots in the game, and whether access is granted to a new player. If access is granted, then the server will return 
+an unique token to the client with which a socket connection can be requested. The client then requests entry into the game 
+with the token and a tunnel is established between the client and the server. Fig 7. shows the game being played by three players, with
+the blue tank being controlled by the current instance.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 5cm] {GameScreenshot.jpg}}
+\caption{Example of Unicast and Broadcast Transmission Architecture}
+\end{figure}
+
+Note that each player has his own score count,a representation of all of the other tanks as well as any bullets which were fire, and finally, a chat area
+in which any player may type a message to send to all other players at any time. To The full list of rules to the game are as follows:
+
+\begin{itemize}
+  \item A Player may move his own tank in any direction at any time.
+  \item A Player may aim the tank and fire a bullet at any time.
+  \item If a Player's bullet intersects another tank, that tank is destroyed and a point added to Player.
+  \item If a Player's tank reaches the red area, their tank will be destroyed and a point deducted.
+  \item A Player may send a message to all other players at any time.
+\end{itemize}
+
+With all of NodeTank's rules layed out, we have the knowledge necessary to start building up the types of test cases and tests we require. 
+In the following sections we will cover the specific testing implementations with the goal of addressing the problem of rigorously testing NodeTank, however, these techniques 
+are easily applicable to other multiplayer games built on the NodeJS platform.
+
+\subsection{Automated Client-side Testing}
+
+As mentioned in the Implementation section, each client has either the ability to affect the simulation in some fashion, or is at least capable of receiving an updated
+version of the simulation. In the case of NodeTank, each client is responsible for controlling one tank according to the aforementioned rules of the game. As previously mentioned,
+instead of simply unit testing in the traditional sense(isolating one function at a time ), but instead attempt to perform a test based upon some use case or rule of the game we will
+ benefit from being able to not only test the individual action on one client, but across all clients.
+Let's take the first rule of the game for example and infer the implications for the entire system
+ of that action being actionable. If a Player A is to move in any direction, then clearly that movement must be rendered in Player A's simuluation at the very least. To allow for interactivity, 
+ the movement must be rendered in the simulation of all other players, which implies that the server must correctly receive, process and send a correct update to all players.
+
+ The proposed implementation called for a testing library to be written, which caters to the peculiarities of a case such as NodeTank while providing generalized functionality for all 
+ applications of the same architecture. Recall the class diagram in Fig 8. layed out the server-side and client-side classes utilized by the game. The authors have implemented a framework
+ under a class entity called "NodeTankTesting", which is coupled into one more more instances of the client-side. The applied changes are visualized in the Fig. 9 daigram. At a high-level,
+ the framework provides mechanisms to start up an instance of NodeTank client in the browser, register tests, programatically control a player and assertions to verify the state of each client.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 5cm] {ClassDiagramWithTesting.jpg}}
+\caption{Modified Class Diagram with Testing Framework}
+\end{figure}
+
+This testing framework relies on the ability to access the internal state of any client instance of NodeTank. The reader may be interested to know that the author of NodeTank 
+elected to utilize the prototype pattern, which is a JavaScript design pattern which allows for great control over inheritance while exposing any closures to outside observers[7]. For example, 
+let's take the Game class from the client-side in consideration. In Fig 10. we can see that the variable "game" is defined into two sections: there is a function declaration, whose body functionally 
+behaves like a constructor, and a prototype assignment, which is a set of methods inherited by all instances of game. The keen reader will note that this is not quite the same classical inheritance
+mechanism utilized by languages such as Java, however we will continue to refer to them as classes as functionally they behave similarly enough.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 5cm] {GameCodeSnippet.jpg}}
+\caption{Snippet of the Game Class}
+\end{figure}
+
+The benefit of the prototype pattern is that we are able to inspect the internal state of any game instance running in the brwoser, and we are also able to programatically induce 
+any inputs such as movement, firing and entering new chat items. Fig 11. is an example of inspecting the entire instance of NodeTank and the position of the player tank programatically.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 2.8cm] {GameInspection.jpg}}
+\caption{Inspecting an Instance of NodeTank}
+\end{figure}
+
+Now that we have a handle to a game instance, we can begin to write some test cases which will allow us to test every client-side functionality of the game. For example, before a player can
+connect to the server, the connection must first be negotiated over a HTTP call. The testing framework has a builtin to send the negotiation request along with the player's desired name, and if the 
+server is not at the maximum player capacity, it will respond with an unique token which will be used from thereon as an identifier. In order to test this functionality, we can programatically request
+the new connection and verify that a token was issued (or denied) as expected.
+In Fig 12.
+we can see the implementation of this test - note that "t" refers to the testing framework and that the "requestToken"
+function requires that a callback be provided, which is called whenever the response for the token request is received.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 2.8cm] {TokenTestSnippet.jpg}}
+\caption{Snippet of Test Case for Requesting a Token}
+\end{figure}
+
+However, a problem remains with this approach in that the test case will work as intended if manually invoked in isolation. Consider that the call itself is asynchronous - we cannot block the 
+main (and only) thread on the client-side while we wait for a response to come back from the server, doing so would pause the client-side simulation at every network interaction and there would be no interactivity!
+Suppose that we wish to have an entire suite of tests, and that some of those tests rely on the previous test completing before being invoked.
+If a string of synchronous function calls would be utilized
+in testing, then we would have no mechanism by which to ensure that test B is only called after test A completed if test A is at all asynchronous. Therefore, a more intelligent design pattern must 
+be leveraged in order to allow the framework to test all cases automatically.
+Fig 13.
+showcases the desired sequence diagram for launching two tests at the correct time without blocking the main thread.
 
 \section{Conclusion}
-\subsection{Future Work}
 
@@
 [1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016, 
-Available from ProQuest Dissertations \& Theses Global. (1881527059).
+Available from ProQuest Dissertations & Theses Global. (1881527059). 
 Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924
@@
 [6] J. Smed, “Aspects of Networking in Multiplayer Computer Games“, Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
-Available: https://www.researchgate.net/publication/269251176\_Aspects\_of\_Networking\_in\_Multiplayer\_Computer\_Games
+Available: https://www.researchgate.net/publication/269251176_Aspects_of_Networking_in_Multiplayer_Computer_Games
+
+[7] A. Osmani "JavaScript Patterns", Book, 2012, Available: https://addyosmani.com/resources/essentialjsdesignpatterns/book/
 \end{document}

### 2020-12-03 paper/PaperDraft2.tex
Merged back Cale's changes

@@
 
-These are all concerns of our case study, NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
+These are all concerns of NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
  to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.
@@
 
-However, simply listing the poistion is not sufficient in order to accurately map the object in space. An object may be rotated 
+However, simply listing the position is not sufficient in order to accurately map the object in space. An object may be rotated 
 around its position. Fig 2. shows a simple example of a car being rotates about the Z axis. The simplest method by which this information can be encoded 
@@
 
-Fig 6 shows our final object state. This will be our basic building blokc when we will discuss the protocol in detail, 
+Fig 6 shows our final object state. This will be our basic building block when we will discuss the protocol in detail, 
 as this will become the data packet which updates clients on the state of the simulation and the objects therein.
@@
 
-\subsection{Trained Model Approach}
+\subsection{Remote Testing}
 
-Discuss the setup for the trained model - the tools and automatic invocation
+\subsubsection{Core RPC Services}Remote testing of the target application is achieved through an adaptable and extensible pair of RPC services.
+Two APIs, 'Data' and 'RemoteCtrl', that enable remote testing and they are capable of being updated and expanded quite easily as the application's range of behaviors grow during its lifetime.
+Each API service is defined in an IDL(Interface Description Language) file.
+Each defines the a service's name followed by generic a list call signatures of the functions that shoould be exposed by the service.
+The IDL offers several plain data types such booleans, floating points, a string type, and signed integers of the typical varying bit-widths.
+Basic C-style structures and enumerations may also be defined to add versatility to the services defined types.
+\subsubsection{RPC Adaptability}As the application grows and new types of interactions and information need to be handled, the same pair of IDL need only minor editing by the maintainer.
+Automatic generations scripts may be rerun at each stage of changing demand.
+The resulting output is a fully-formed supporting library in the target programming language of choice for, both, the client and server sides of each RPC service.
+The RPC-server half of each API is included and/or linked to from the simulation's server to allow both services awareness of and access to all necessary data of the simulation's clients.
+In the event of new or changing data types, the client simulation needs only to be rebuilt in the case of a compiled-language and no changes are required for interpreted languages.
+In the case of new or changing functions, the auto-generated RPC handlers need only be given function bodies by the tester.
+Building remote testing utilities for the simulation is easily done thanks to this process, as there are no dependencies between the programming language of the simulation's server and the RPC client.
+The RPC service itself manages all translation between native data types of the server and it's RPC client.
+This means the RPC service manages the serialization/deserialization and transport of all function arguments and return values, byte-order translation between differing host hardware, and member alignment between differing host operating environments.
+All these features allow for a simulation written in javascript, C++, Java, Python, C\#, etc.
+to agnostically cooperate with any client written in any other supported language and host operating environemnt.
+\subsubsection{Distributibility}With an underlying TCP or UDP transport layer, this remote testing strategy allows for a wide range of geographical testing configurations to be thuroughly explored.
+Testing and examination of the system may be performed in a close-proximity LAN configuration, or the simulation server and its clients may be much more georgraphically separated, communicating over the Internet with one another and the testing client itself.
 
@@
 version of the simulation. In the case of NodeTank, each client is responsible for controlling one tank according to the aforementioned rules of the game. As previously mentioned,
-instead of simply unit testing in the traditional sense(isolating one function at a time ), but instead attempt to perform a test based upon some use case or rule of the game we will
+instead of simply unit testing in the traditional sense(isolating one function at a time), but instead attempt to perform a test based upon some use case or rule of the game we will
  benefit from being able to not only test the individual action on one client, but across all clients.
@@
 
+\subsection{Remote RPC Services}
+\subsubsection{Remote Testing Service}
+\paragraph{Hooks into the javascript testing framework}
+\subsubsection{Remote Control Service}
+\paragraph{Injecting user input}
+\paragraph{Extracting the rendered environment}
+
 \section{Conclusion}
@@
 
+\subsection{Future Work}
+
 \section{References}
 [1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016, 
-Available from ProQuest Dissertations & Theses Global. (1881527059). 
+Available from ProQuest Dissertations \& Theses Global. (1881527059). 
 Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924
@@
 [6] J. Smed, “Aspects of Networking in Multiplayer Computer Games“, Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
-Available: https://www.researchgate.net/publication/269251176_Aspects_of_Networking_in_Multiplayer_Computer_Games
+Available: https://www.researchgate.net/publication/269251176\_Aspects\_of\_Networking\_in\_Multiplayer\_Computer\_Games
 

### 2020-12-03 paper/PaperDraft2.tex
Added support for JS code blocks

@@
 \usepackage{xcolor}
+\usepackage{listings}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+%Customize a bit the look
+\lstset{ %
+backgroundcolor=\color{white}, % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
+basicstyle=\footnotesize, % the size of the fonts that are used for the code
+breakatwhitespace=false, % sets if automatic breaks should only happen at whitespace
+breaklines=true, % sets automatic line breaking
+captionpos=b, % sets the caption-position to bottom
+commentstyle=\color{mygreen}, % comment style
+deletekeywords={...}, % if you want to delete keywords from the given language
+escapeinside={\%*}{*)}, % if you want to add LaTeX within your code
+extendedchars=true, % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
+frame=single, % adds a frame around the code
+keepspaces=true, % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
+keywordstyle=\color{blue}, % keyword style
+% language=Octave, % the language of the code
+morekeywords={*,...}, % if you want to add more keywords to the set
+numbers=left, % where to put the line-numbers; possible values are (none, left, right)
+numbersep=5pt, % how far the line-numbers are from the code
+numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
+rulecolor=\color{black}, % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
+showspaces=false, % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
+showstringspaces=false, % underline spaces within strings only
+showtabs=false, % show tabs within strings adding particular underscores
+stepnumber=1, % the step between two line-numbers. If it's 1, each line will be numbered
+stringstyle=\color{mymauve}, % string literal style
+tabsize=2, % sets default tabsize to 2 spaces
+title=\lstname % show the filename of files included with \lstinputlisting; also try caption instead of title
+}
+
+\definecolor{darkgray}{rgb}{.4,.4,.4}
+\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
+
+\lstdefinelanguage{JavaScript}{
+keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
+keywordstyle=\color{blue}\bfseries,
+ndkeywords={class, export, boolean, throw, implements, import, this},
+ndkeywordstyle=\color{darkgray}\bfseries,
+identifierstyle=\color{black},
+sensitive=false,
+comment=[l]{//},
+morecomment=[s]{/*}{*/},
+commentstyle=\color{purple}\ttfamily,
+stringstyle=\color{red}\ttfamily,
+morestring=[b]',
+morestring=[b]"
+}
+
+\lstset{
+language=JavaScript,
+extendedchars=true,
+basicstyle=\footnotesize\ttfamily,
+showstringspaces=false,
+showspaces=false,
+numbers=left,
+numberstyle=\footnotesize,
+numbersep=9pt,
+tabsize=2,
+breaklines=true,
+showtabs=false,
+captionpos=b
+}
+
 \begin{document}
@@
 
+\begin{lstlisting}[language=JavaScript]
+    let id2 = t.registerTest("testCase2");
+    let test2 = (resolve, reject) => {
+        t.requestToken(player1Name, (token) => {
+            if (t.assertExists(token)) {
+                t.passTest(id2);
+                resolve ? resolve() : null;
+            }
+            else {
+                t.failTest(id2);
+                resolve ? resolve() : null;
+            }
+        });
+    };
+
+\end{lstlisting}
+
 However, a problem remains with this approach in that the test case will work as intended if manually invoked in isolation. Consider that the call itself is asynchronous - we cannot block the 

### 2020-12-04 paper/PaperDraft2.tex
adding control service descriptions

@@
 showtabs=false,
-captionpos=b
+captionpos=b,
+linewidth=.46\textwidth,
+xleftmargin=.2cm
 }
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics [width = 9cm, height = 5cm] {ClassDiagramWithTesting.jpg}}
+\centerline{\includegraphics [width = 6cm, height = 9cm] {Class2.0.PNG}}
 \caption{Modified Class Diagram with Testing Framework}
@@
 Within \textit{gameCore} the RPC host objects are setup each to operate within their own thread, alongside the game's primary servers.
+
+\begin{lstlisting}[language=JavaScript,caption={In this example, the thrift is used to create a server for the  'dataInterface' service.
+It then lists two skeleton functions to handle 'GetGameData' and 'ExecuteTests' functions.}]
+dataServer = thrift.createServer(dataInterface,{
+  GetGameData:     function(){
+      let game_data = { /*meaningful code*/ };
+      return game_data;
+    },
+  ExecuteTests:    function(arg1,arg2){
+      // Custom handler code goes here
+    },
+    .
+    .
+});
+dataServer.listen(9091);
+\end{lstlisting}
+This RPC server instantiation serves as the primary hook into the innards of the game, and is how the queries into the internal game objects' states are achieved.
+
 \subsubsection{Remote Control Service}
+The control service is implemented in the same manner.
+Instead of focusing on extracting information from the server, the remote control service operates on the server's internals by calling its internal functions, even supplying arguments to them from the outside.
+Functions exported from the module in \textit{socket-manager.js} are at the disposal as well, including those for making websocket calls to client instances.
+This extends the reach of the control service even further, allowing it to pass commands along to client code, for example, initiating the client to perform functional tests upon itself and to alert the server after it has finished.
+The final type of control interaction provided by the service is launch the remote testing service's server, which is not running by default.
+This makes the the control service client a dependency of any remote testing client.
+
+\subsection{Remote Control Service's Missing Components}
 \paragraph{Injecting user input}

### 2020-12-04 paper/PaperDraft2.tex

@@
 
-\subsection{Remote Control Service's Missing Components}
+\subsection{Remote Control Service's Supporting Role}
+The additional goal of the testing framework alongside the remote testing utilities to to support extended periods of software testing.
+The motivation for this being to allow testers to discover unintended and most likely unwanted effects of long-term execution times of their software.
+Through manual testing of NodeTank, we discovered that spent bullet objects were not being destroyed after leaving the rendered region of the game.
+This build up, over time, led to considerable sluggishness.
+It is these emergent properties and behaviors that are often hard to test for with a human in the loop, and can go undiscovered for quite some time.
+To solve this problem we had proposed the idea of implementing an Agent play the NodeTank game for extended periods of time that would otherwise be unrealistic to expect of a human player.
+Allowing the game to run for extended periods of time with external interaction would allow for fuller and more expansive sweep of the ranging states of gameplay.
+Traditionally in reinforcement learning, an abstract set of game states would be established, and for those states, corresponding actions that would be appropriate for a player to take reinforced by a reward.
+This mapping of states and actions would be stored in what's known as a Q-table.
+As the agent explores various actions in the environment, it updates the values in the Q-table to reflect those actions that yielded the maximum cummulative reward.
+In the case of gaming, especially those rendered in 3-dimensions, there is substantial state explosion that occurs when taking into account all of the possible positions, orientations, objects, and object interactions.
+Storing these states and actions becomes very impractical very quickly.
+To overcome this problem, the Q-table will be replaced with a deep-query neural network, or DQN.
+The additional training time required for a DQN is a trade-off made for the constant memory that would otherwise grow exponentially with a Q-table.
+Additionally, the DQN would, after being trained, be able to select actions in response to environmental observations it has never seen before, which is another major advantage over the traditional Q-table.
+Pushing environmental information to and receiving player input from the DQN is a major intended role of the remote control service.
 \paragraph{Injecting user input}
+The remote control service has several functions that allow for injecting input that would otherwise come from a player, directly into the \textit{gameLoop.js} singleton.
+This includes RPC calls for positional movement, rotating, and firing the NodeTank tanks.
+It is the inputs to these functions that would be the direct outputs of the DQN's fully-connected layer.
+This output would be fed to the remote control service's functions following each of the DQN's action predictions.
 \paragraph{Extracting the rendered environment}
+To further facilitate the training of this agent, the remote control service is meant to forward environmental observations to the agent.
+These observations are in the form of a snapshot of the most recently rendered frame of the game.
+This image is encoded in a base-64 string and sent to the server where it waits to be requested by the remote control service.
+After receiving and decoding the base-64 string, the image would be scaled down to more ideal dimensions for input into the DQN.
+As this observation data propgates forward through the convolutional layers, more and more features are extracted before finally being flattened and fed into the full-connected layers of the network to decide upong the most ideal actions to output.
+The results of those actions amount to a reward in the game's environment, in our case, the players score which will drop if the player is hit by an enemy, and rise if the players hits an enemy.
+In actual implementation, the environmental observations, chosen actions, and environmental reward are stored in what's known as a \textit{replay memory}.
+This \textit{replay memory} is vital to the stable learning of the DQN, as memories have to chosen in random batches for processing by the DQN to alleviate the high temporal correlation of processing back-to-back frames of gameplay.
 

### 2020-12-04 paper/PaperDraft2.tex
Paper updates

@@
 \begin{figure}[htbp]
-\centerline{\includegraphics [width = 6cm, height = 9cm] {Class2.0.PNG}}
+\centerline{\includegraphics [width = 6cm, height = 9cm] {classv2.PNG}}
 \caption{Modified Class Diagram with Testing Framework}
@@
 elected to utilize the prototype pattern, which is a JavaScript design pattern which allows for great control over inheritance while exposing any closures to outside observers[7]. For example, 
-let's take the Game class from the client-side in consideration. In Fig 10. we can see that the variable "game" is defined into two sections: there is a function declaration, whose body functionally 
+let's take the Game class from the client-side in consideration.
+In Listing 1, we can see that the variable "game" is defined into two sections: there is a function declaration, whose body functionally
 behaves like a constructor, and a prototype assignment, which is a set of methods inherited by all instances of game. The keen reader will note that this is not quite the same classical inheritance
@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics [width = 9cm, height = 5cm] {GameCodeSnippet.jpg}}
-\caption{Snippet of the Game Class}
-\end{figure}
+\begin{lstlisting}[language=JavaScript,caption={Snippet of the Game Class}]
+    game = function(canvas, socket, token, name) {
+		this.canvas = canvas;
+		this.socket = socket;
+		this.token = token;
+		this.name = name;
+		this.initCallback = undefined;
+		//...
+	};
+
+game.prototype = {
+    //set up an instance of the game
+    init: function(callback) {
+        this.initCallback = callback;
+        this.configSocket();
+        console.log(this.name);
+        this.socket.emit('joinGame', {
+            token: this.token,
+            name: this.name
+        });
+    },
+\end{lstlisting}
 
@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics [width = 9cm, height = 2.8cm] {TokenTestSnippet.jpg}}
-\caption{Snippet of Test Case for Requesting a Token}
-\end{figure}
-
-\begin{lstlisting}[language=JavaScript]
+\begin{lstlisting}[language=JavaScript,caption={Snippet of Test Case for Requesting a Token}]
     let id2 = t.registerTest("testCase2");
@@
     };
-
 \end{lstlisting}

### 2020-12-04 paper/PaperDraft2.tex
Paper update

@@
 \section{Approach}
-Our approach is to develop a testing framework for NodeTank will combine abstract testing of models, unit testing, and functional testing into a single, yet modular, 
+Our approach is to develop a generalized framework for NodeJS will combine abstract testing of models, unit testing, and functional testing into a single, yet modular, 
 utility. The effort of functional testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility 
@@
 
-\subsection{Automated Functional Testing}
+\subsection{Automated Client-side Testing}
 
 The first testing scenario we will consider is to allow the system to automatically play the game in order to test a set of pre-defined set of actions.
-For example, we can programatically interact with the game directly in order to control one of the player tanks. With the system having control over a player character, 
-we can individually test the different aspects of the game: movement, shooting, respawning etc... This type of autmated testing could be invoked on an individual developer's 
-machine in order to test each function of the game as its being developed.
+For example, let's assume that we may programatically interact with the simulation directly in at least one of the client instances. With the system having control over a client simulation, 
+we can individually test the different interactions with the simulation. This type of autmated testing could be invoked on an individual developer's 
+machine in order to test each function of the system as its being developed or modified. If the simulation has a visual representation, then perhaps it will be beneficial to 
+visually show any changes to the simulation state to the viewer as the tests are being invoked.
 
-However, we may take this testing even further and consider that since the game runs within the browser, we would be able to tap into any concurrent client simulation. This 
-has the implication that we would be able to inspect the state of each client concurrently.
+Consider the architecture diagram in Fig. 1, wherein each client has a two-way connection to the server. The client may push an update to the simulation state, and likewise each
+client can receive the updated state at any time.
 
@@
 an unique token to the client with which a socket connection can be requested. The client then requests entry into the game 
-with the token and a tunnel is established between the client and the server. Fig 7. shows the game being played by three players, with
+with the token and a tunnel is established between the client and the server. Fig 8. shows the game being played by three players, with
 the blue tank being controlled by the current instance.
@@
 \centerline{\includegraphics [width = 9cm, height = 5cm] {GameScreenshot.jpg}}
-\caption{Example of Unicast and Broadcast Transmission Architecture}
+\caption{Screenshot of the Game with Three Players}
 \end{figure}

### 2020-12-04 paper/PaperDraft2.tex
Paper Update

@@
 Consider the architecture diagram in Fig. 1, wherein each client has a two-way connection to the server. The client may push an update to the simulation state, and likewise each
-client can receive the updated state at any time.
+client can receive the updated state at any time. If we are to perform an automated functional test, then it would be sufficient to tap into one of the clients, and simply invoke 
+some change in that client. However, while this may be sufficient to verify that operability of the functions pertaining to a client, it does not guarantee that the entire system 
+is indeed working as intended, namely that all other clients are receiving and rendering the updates correctly. Fig 8. shows our proposed approach to this problem. Note that a "Testing Framework"
+entity is created, which is communicating to each client, and would have the ability to programatically invoke a client change, and likewise to programatically listen to any changes in each client.
+With these capabilities in mind, the framework would be capable of provoking a change in a client and then verify the change in all other clients for correctness.
 
-\subsection{Automated Unit Testing}
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 6cm, height = 6cm] {images/ClientSideFrameworkDiagram.jpg}}
+\caption{Architecture with Client-side Testing Framework}
+\end{figure}
+
+\subsection{Automated Full-stack Testing}
 

### 2020-12-04 paper/PaperDraft2.tex
Paper changes

@@
 \section{Approach}
-Our approach is to develop a generalized framework for NodeJS will combine abstract testing of models, unit testing, and functional testing into a single, yet modular, 
-utility. The effort of functional testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility 
+Our approach is to develop a generalized framework for NodeJS will combine client-side unit, full-stack, and remote testing into a single, yet modular, 
+utility. The effort of client-side unit testing will involve the synchronization of timing of outputs from the server as well as the clients involved. The testing utility 
 should be distributable just as the software being tested and a means of distributing and launching a test should be runnable from a single test location. Any data and 
@@
 an interpreted language to run test suites end to end. Firstly, we will investigate an approach similar to Ariyurek et al[2] in order to develop an automated 
-system to test the application as well as to automatically find problems with it. Secondly, the fact that the application in its unobstructed build state will have
+system to test the application as well as to automatically find problems with it. Secondly, the assumption that the application will be its unobstructed build state implies
 its internal state visible and inspectable from the outside. That is to say, if we were to run multiple client simulations concurrently, we would be able to inspect 
@@
 perspective of each client. Likewise, the fact that we could control each client independently, we will be able to gauge the susceptibility of the simulation to erroneous 
-or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients.
+or malicious data by willfully introducing it to one client, and checking if the erroneous data was propagated to the other clients. Lastly, we have the option of checking
+each client's internal state with the internal state of the server to ensure all simulations are synchronized correctly.
+
+The following sections will describe three different approaches to testing a generalized asynchronous simulation, followed by the actual implementation of the framework.
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics [width = 6cm, height = 6cm] {images/ClientSideFrameworkDiagram.jpg}}
+\centerline{\includegraphics [width = 6cm, height = 5.5cm] {images/ClientSideFrameworkDiagram.jpg}}
 \caption{Architecture with Client-side Testing Framework}
@@
 
-To be developed
+The testing layout described in the previous section is a very good approach in ensuring the integrity of an individual client, it however does not take the state of the server into account.
+For clarity, let's assume that we were to run a simulation for some amount of time, and during that amount of time, each client has performed a set of actions.
+Over time, there exists a possibility that
+although each client may have correctly reflected a single action from another client, there
 

### 2020-12-04 paper/PaperDraft2.tex
Paper update

@@
  to be the most significant. Combining strong unit and integration testing inside the server, each simulation needs to be tested for usability, compatibility, and 
- reliability. Likewise, since the integrity of the simulation is paramount, susceptibility to malicious or incorrect information fed into the system  must be mitigated, 
- and as such, we will explore mechanisms by which test the system.
+ reliability. Likewise, since the corectness and robustness of the simulation is paramount, we will also explore mechanisms by which to perform end to end testing of such simulations.
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics [width = 6cm, height = 5.5cm] {images/ClientSideFrameworkDiagram.jpg}}
+\centerline{\includegraphics [width = 6cm, height = 5cm] {images/ClientSideFrameworkDiagram.jpg}}
 \caption{Architecture with Client-side Testing Framework}
@@
 Over time, there exists a possibility that
-although each client may have correctly reflected a single action from another client, there
+although each client may have correctly reflected a single action from another client, the simulation of each client may have become out of sync. The reason for such a possibility is that in most 
+asynchronous simulations a certain level of interpolation is introduced for each client. For example in a typical game application, when Player 1 performs an action, the local
+rendering will start to show the movement before a confirmation from the server is received in order to mask any underlying latency. Since every client will perform its own interpolation, 
+there exists the possibility that all clients will become out of sync over time.
+
+In order to account for this possible discrepancy, we may modify the diagram in Fig. 8 to allow the testing framework an entrypoint into the server. The reasoning being that we may programatically
+control multiple clients for some amount of time and then verify the internal state of the server to the internal state of each client. Fig. 9 shows the modified diagram, note that the connection
+from the framework to the server is meant to pull the internal state of the server for comparison with all connected clients. For easy integration, it may be assumed that the Testing Framework
+is the same entity for both test scenarios.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 6cm, height = 5cm] {images/FullStackTestingDiagram.jpg}}
+\caption{Architecture with Full-stack Testing Framework}
+\end{figure}
 

### 2020-12-04 paper/PaperDraft2.tex
One more paper update

@@
 In order to circumvent this, information about how fast the object is moving may be encoded such that an extrapolation between snapshots may occur. This velocity attribute 
-is split into two segments; the liear velocity, which is the change in position across the Cartesian system, and angular velocity, which is the change in orientation. 
+is split into two segments; the linear velocity, which is the change in position across the Cartesian system, and angular velocity, which is the change in orientation. 
 Each one of these attributes may be encoded in a three dimensional vector(Fig 1).
@@
 
-The first testing scenario we will consider is to allow the system to automatically play the game in order to test a set of pre-defined set of actions.
+The first testing scenario we will consider is to allow the system to automatically control the simulation in order to test a set of pre-defined actions.
 For example, let's assume that we may programatically interact with the simulation directly in at least one of the client instances. With the system having control over a client simulation, 
@@
 an unique token to the client with which a socket connection can be requested. The client then requests entry into the game 
-with the token and a tunnel is established between the client and the server. Fig 8. shows the game being played by three players, with
+with the token and a tunnel is established between the client and the server. Fig. 10 shows the game being played by three players, with
 the blue tank being controlled by the current instance.
@@
 
-With all of NodeTank's rules layed out, we have the knowledge necessary to start building up the types of test cases and tests we require. 
+As alluded to earlier, NodeTank uses a client-server architecture, however with a couple of slight distinctions. The first being that although the clients and the server
+communicate state changes over a two-way socket, the server also has several RESTful HTTP endpoints which allow connection negotiations and debugging data transfers to occur. 
+Fig. 11 showcases the architectural layout - note that in addition to the socket, the client may request some data over a HTTP call, and the server is then able to respond to 
+this call individually. The usefulness of this approach will become evident when attempting to inspect the internal state of the server.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 6cm] {images/testingSchemaArch.png}}
+\caption{The Architecture of NodeTank}
+\end{figure}
+
+With all of NodeTank's rules and structure layed out, we have the knowledge necessary to start building up the types of test cases and tests we require. 
 In the following sections we will cover the specific testing implementations with the goal of addressing the problem of rigorously testing NodeTank, however, these techniques 
@@
  applications of the same architecture. Recall the class diagram in Fig 8. layed out the server-side and client-side classes utilized by the game. The authors have implemented a framework
- under a class entity called "NodeTankTesting", which is coupled into one more more instances of the client-side. The applied changes are visualized in the Fig. 9 daigram. At a high-level,
+ under a class entity called "NodeTankTesting", which is coupled into one more more instances of the client-side. The applied changes are visualized in the Fig. 11 diagram. At a high-level,
  the framework provides mechanisms to start up an instance of NodeTank client in the browser, register tests, programatically control a player and assertions to verify the state of each client.
@@
 The benefit of the prototype pattern is that we are able to inspect the internal state of any game instance running in the brwoser, and we are also able to programatically induce 
-any inputs such as movement, firing and entering new chat items. Fig 11. is an example of inspecting the entire instance of NodeTank and the position of the player tank programatically.
+any inputs such as movement, firing and entering new chat items. Fig 12. is an example of inspecting the entire instance of NodeTank and the position of the player tank programatically.
 
@@
 the new connection and verify that a token was issued (or denied) as expected.
-In Fig 12.
-we can see the implementation of this test - note that "t" refers to the testing framework and that the "requestToken"
+In Listing 1 we can see the implementation of this test - note that "t" refers to the testing framework and that the "requestToken"
 function requires that a callback be provided, which is called whenever the response for the token request is received.
@@
 If a string of synchronous function calls would be utilized
-in testing, then we would have no mechanism by which to ensure that test B is only called after test A completed if test A is at all asynchronous. Therefore, a more intelligent design pattern must 
+in testing, then we would have no mechanism by which to ensure that test B is only called after test A completed assuming test A is at all asynchronous.
+Therefore, a more intelligent design pattern must
 be leveraged in order to allow the framework to test all cases automatically.
-Fig 13.
-showcases the desired sequence diagram for launching two tests at the correct time without blocking the main thread.
+
+In order to account for the client application only having one thread, we must implement the framework using a callback pattern. S. Kyle[8] describes callback as a function which 
+"is acting as a callback, because it serves as the target for the event loop to “call back into” the program, whenever that item in the queue is processed.". For example, the simplest 
+use case for a callback would be whenever a HTTP call is made to a remote resource. The main thread asks for the remote resource, and provides a callback function which is to be called whenever
+a response comes from the server. Before this callback is called, the main thread may continue executing other items, in the example of NodeTank, the rendering and interactivity. However, a pure
+callback is not sufficient in that it becomes increasingly unwieldy as more dependent calls are stacked. Luckily, JavaScript has a special type of callback mechanism called a Promise, which allows 
+us to call asynchronous functions in the correct order so long as we can correctly control when the next function should be called.
+Listing 3 shows all test cases being invoked in the correct sequence.
+
+\begin{lstlisting}[language=JavaScript,caption={Snippet of Automatically Invoking Test Cases in Order}]
+    let test1P = new Promise(test1).then(() => {
+                return new Promise(test2);
+            }).then(() => {
+                return new Promise(test3);
+            }).then(() => {
+                return new Promise(test4);
+            }).then(() => {
+                return new Promise(test5);
+			//....
+			});
+\end{lstlisting}
+
+The Promise mechanism provides yet another benefit to us, namely that we have the ability to manually kick off any individual test function in conjuction with doing so automatically. 
+Refering back to Listing 2, note that on line 6 we're checking for the existence of a function named "resolve", and if it exists we call it. This function is the mechanism which whe signal 
+to the Promise that the current function has executed and that the next function call in the sequence may be made.
+
+Putting all of these features together, we have arrived at all of the tools necessary to build the framework to the state in which it can automatically start a game instance, control a player, 
+and ultimately verify the game across all instances. The reader is encouraged to download and inspect the Testing Framework for the exact implementation of how instances are set up,
+how assertions are defined how all of these are coupled in an asynchronous manner. Fig. 13 showcases 18 separate test cases which passed and were invoked automatically. As mentioned 
+earlier, we thought it prudent to also visually show any changes should the user chose to perform a visual inspection. Likewise, the user also has the ability to manually invoke
+any individual test case.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 6cm] {images/FullClientSideTesting.jpg}}
+\caption{Full Client-side Testing Implementation with NodeTank}
+\end{figure}
 
@@
 
-[7] A. Osmani "JavaScript Patterns", Book, 2012, Available: https://addyosmani.com/resources/essentialjsdesignpatterns/book/
+[7] A. Osmani "JavaScript Patterns", Book, 2012, pp.35, Available: https://addyosmani.com/resources/essentialjsdesignpatterns/book/
+
+[8] S. Kyle "You Don't Know JS: Async \& Performance ", Book, 2015, pp.41
 \end{document}

### 2020-12-04 paper/PaperDraft2.tex
Verbiage change
Almost the last paper changes

@@
 and ultimately verify the game across all instances. The reader is encouraged to download and inspect the Testing Framework for the exact implementation of how instances are set up,
-how assertions are defined how all of these are coupled in an asynchronous manner. Fig. 13 showcases 18 separate test cases which passed and were invoked automatically. As mentioned 
-earlier, we thought it prudent to also visually show any changes should the user chose to perform a visual inspection. Likewise, the user also has the ability to manually invoke
+how assertions are defined how all of these are coupled in an asynchronous manner. Fig. 13 showcases 18 separate passing test cases which were invoked automatically performed on 4 distinct instances.
+As mentioned earlier, we thought it prudent to also visually show any changes should the user chose to perform a visual inspection. Likewise, the user also has the ability to manually invoke
 any individual test case.
@@
 \end{figure}
+
+\subsection{AutomatedFull-stack Testing}
+
+Refering back to the implementation, we have an incentive to also test the entire stack. In order to provide access to the server, we proposed another interface from the Testing Framework
+to the server in order to pull the internal state of the simulation. However, for this type of testing to be meaningful, we cannot simply start seperate instances of NodeTank and then immediately 
+verify the state. To fully leverage this type of testing, we must have a mechanism by which to perform changes to the game from each instance for some amount of time before the actual comparison 
+between clients and server may take place.
+
+Firstly, we may build off of the framework we've developed for client-side testing as it has already solved the problem of programatically controlling a client in isolation and verifying the internal
+state of a client. With the goal of applying a change of state to all clients, we have the solution of applying a random movement, shooting a random target, and a random shooting interval
+for each client.
+These random events are generated again after a random amount of time, until the total amount of elapsed time reaches an upper bound in seconds, with all of these actions encompasing a "tick".
+A random number of ticks are performed up to a certain upper bound, and after all ticks are executed, we may then fetch the internal state of the server and verify it against all instances.
+
+\begin{lstlisting}[language=JavaScript,caption={Snippet of Invoking a Random Number of Automatic Tests}]
+        let startTests = () => {
+        currentTick = 0;
+        currentMaxTicks = randomInRange(ticksBetweenChecks) + 1;
+        runTest = true;
+        resetAllCells();
+        clearMessages();
+        setInterval(() => {
+            runIteration()
+        }, tickLength * 1000);
+
+        runIteration();
+    };
+\end{lstlisting}
+
+Listing 4 showcases how each tick is invoked.
+Firstly, the initial values of our tracking variables are set, however lines 11 and 15 are of interest.
+Line 11 again uses a subset of the callback pattern
+to asyncronously call the "runIteration" function after each tick length expires, and line 15 invokes the function immediatetly so that we do not have to wait for the tickLength to pass before the first
+test case is kicked off.
+
+\begin{lstlisting}[language=JavaScript,caption={Snippet of runIteration}]
+    let runIteration = () => {
+        if (runTest) {
+            console.log("Tick " + currentTick);
+            currentTick++;
+            stopAllMovement();
+            stopAllActions();
+            t.setRandomMovement(gameInstance1);
+            gameInstance1.messageObj.queuedText = messageSet[randomInRange(messageSet.length - 1)];
+
+            //set each instance to shoot at another random instance
+            interval1 = setInterval(() => {
+                //aim at something other than itself
+                let target = 0;
+                while (target === 0) {
+                    target = randomInRange(3);
+                }
+                gameInstance1.playerTank.setLookAt(instanceArray[target].playerTank.group.position);
+                gameInstance1.clicked = true;
+
+                stopAllMovement();
+                t.setRandomMovement(gameInstance1);
+            }, randomInRange(tickLength) * 1000);
+\end{lstlisting}
+
+Finally,
 

### 2020-12-05 paper/PaperDraft2.tex
Paper Update

@@
             }, randomInRange(tickLength) * 1000);
+
+			//......
+			if (currentTick >= currentMaxTicks) {
+                verify();
+            }
 \end{lstlisting}
 
-Finally,
+Finally, Listing 5 showcases the "runIteration" function, which is called once for each tick.
+Lines 5 and 6 clear all movement which was set in the previous tick - this is part of the Testing Framework
+and is implementation specific.
+Line 7 sets a random movment for the first game instance and line 12 set a sub interval in which a random other tank is selected to be targeted and to be fired upon at a
+random interval. The reader may note that multiple sub intervals are set for each tank in each tick in order to maximize randomization. Finally, on line 26, once all ticks have been ran,
+we can invoke the verify function (Listing 6).
+
+\begin{lstlisting}[language=JavaScript,caption={Snippet of Verification Code}]
+    let verify = () => {
+        runTest = false;
+        fetchServerSnapshot();
+    };
+	fetchServerSnapshot = () => {
+        t.HTTPRequest("POST", "/debug/getGameState", {}, (response) => {
+            if (response.success) {
+                checkAgainstInstances(response.data);
+            }
+        });
+    };
+\end{lstlisting}
+
+After all of the ticks have been ran, we may leverage a debugging interface opened in the server(Listing 6, line 6), which returns the internal snapshot of the simulation from the server. 
+Using this snapshot, we will verify that the server copy of each tank's score, location and chat messages matches the authoritative snapshot. Putting it all together, we arrive at Fig. 15, which 
+has all of the client instances performing the random actions and a representation of the test results. In this case, the framework has detected a discrepancy of Player 2's position on his own
+instance.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 9cm, height = 6cm] {images/FullFullStackTesting.jpg}}
+\caption{Full-stack Testing Implementation with NodeTank}
+\end{figure}
 

### 2020-12-05 paper/PaperDraft2.tex
Adding some to future work

--- 2020-12-04 paper/PaperDraft2.tex
@@
 \subsection{Future Work}
-
+Future work would begin with a fully-realized implementation of the synthetic agent for, both, facilitating extended runtime data collection and testing as well as exploring the a fuller range of the game's runtime states.
+The testing utility would then include several pre-trained models minimally capable of navigating 2 and 3 dimensional environments while avoiding collisions with a generic interface for the tester(s) to provide functions specific to their environment for detecting states of collision as well as their reward signals unique to their environments.
 \section{References}

### 2020-12-05 paper/PaperDraft2.tex
removed line of text
Fixed Figure references Removed the section on game model since we never used it

--- 2020-12-05 paper/PaperDraft2.tex
@@
 In the real world, we have object which we can look at and interact with. When such objects are created in a 3D renderer,
-some data must be modeled about the object. For simplicity, we will only consider a Cartesian coordinate system(Fig 2), in which points are mapped 
+some data must be modeled about the object. For simplicity, we will only consider a Cartesian coordinate system(Fig. 4), in which points are mapped 
 by numerical coordinates along three perpendicular lines(axes). Intuitively, the positional information may be expressed in terms of a displacement 
-along each one of the three axes (X, Y, Z). As such, a simple vector with three components can encode this information(Fig 1.):
+along each one of the three axes (X, Y, Z). As such, a simple vector with three components can encode this information(Fig. 3):
 
@@
 However, simply listing the position is not sufficient in order to accurately map the object in space. An object may be rotated 
-around its position. Fig 2. shows a simple example of a car being rotates about the Z axis. The simplest method by which this information can be encoded 
+around its position. Fig. 5 shows a simple example of a car being rotates about the Z axis. The simplest method by which this information can be encoded 
 is to use another three component vector to keep track of the roation around each axis, and then apply each rotation to each axis in a cascading fashion. 
@@
 but without the gimbal lock limitation which would cause rotation behavior should it occur. In short, this quaternion may be expressed as a four dimensional
-vector, similar to the one expressed in Fig 1., but with an extra component, \textit{w}.
+vector, similar to the one expressed in Fig. 3, but with an extra component, \textit{w}.
 
@@
 is split into two segments; the linear velocity, which is the change in position across the Cartesian system, and angular velocity, which is the change in orientation. 
-Each one of these attributes may be encoded in a three dimensional vector(Fig 1).
+Each one of these attributes may be encoded in a three dimensional vector(Fig 3).
 
@@
 
-Fig 6 shows our final object state. This will be our basic building block when we will discuss the protocol in detail, 
-as this will become the data packet which updates clients on the state of the simulation and the objects therein.
-
-\subsection{Game Model}
-
-The protocol workflow has been described at a very high level, but it is agnostic to the specific game and the rules associated with it. The 
-player is modeled by a tank object. This tank object has a few properties associated with it: alive, outOfBounds, score. The alive state 
-dictates whether the tank is on the playing field - given that in our rules we have established that being shot simply leads to a respawn, 
-this state is only used to indicate that a respawn must occur and that the other player's score is incremented. The outOfBounds attribute is true 
-when the player steps outside of the game field, which leads to alive being set to false and score being decremented. The score attribute 
-keeps track of the player's current score.
-
-A keen observer would note that a player's tank has many more attributes that those listed above. Rezin et al [3] utilized model checking 
-on a multiplayer game, and they came up with an attribute list which contained all variables that would change over the course of the game.
-The attributes are tied into parameters, which are constants set at the beginning of the game. For example, a player's tank can be modeled
-as a parameter with attrbutes X position, Y position, Z position, lookAt, score, alive, outOfBounds. The limitation of using this approach is that 
-if an object's position is utilized in checking the model, the list of all possible state combinations would be too large to ever compute due 
-to the size of the game field having granularity in the tens of millions and the total number of possible lookAt locations also being in the millions.
-
-With these considerations in mind, model checking has also been overlooked in favor of utilizing automated testing to test the 
-game directly for consistency in its rules. One thing of note is that the formal definition of the game rules for example, a valid x coordinate,
-is syntactically equivalent to the check the game logic would perform; therefore writting a model checking program is redundant in this specific 
-case. Fig 11 shows the formal definition along with the implementation of the rule.
-
-\begin{figure}[htbp]
-\[ (W_{xmin} \leq T_{x} \leq W_{xmax}) \]
-\[ !(playerTanks[k].obj.position.x < xMin ||\]
-\[ playerTanks[k].obj.position.x > xMax) \]
-\caption{Formal Rule and Implementation of Valid X coordinate}
-\end{figure}
+Fig. 6 shows our final object state. This will be our basic building block for all objects in not only a generic multiplayer game simulation, 
+but also our case study, NodeTank. When considering testing, the primary attribues which are sent via server updates to the clients are position,
+orientation and a game specific attribute, score.
 
@@
 some change in that client. However, while this may be sufficient to verify that operability of the functions pertaining to a client, it does not guarantee that the entire system 
-is indeed working as intended, namely that all other clients are receiving and rendering the updates correctly. Fig 8. shows our proposed approach to this problem. Note that a "Testing Framework"
+is indeed working as intended, namely that all other clients are receiving and rendering the updates correctly. Fig 7. shows our proposed approach to this problem. Note that a "Testing Framework"
 entity is created, which is communicating to each client, and would have the ability to programatically invoke a client change, and likewise to programatically listen to any changes in each client.
@@
 
-In order to account for this possible discrepancy, we may modify the diagram in Fig. 8 to allow the testing framework an entrypoint into the server. The reasoning being that we may programatically
-control multiple clients for some amount of time and then verify the internal state of the server to the internal state of each client. Fig. 9 shows the modified diagram, note that the connection
+In order to account for this possible discrepancy, we may modify the diagram in Fig. 7 to allow the testing framework an entrypoint into the server. The reasoning being that we may programatically
+control multiple clients for some amount of time and then verify the internal state of the server to the internal state of each client. Fig. 8 shows the modified diagram, note that the connection
 from the framework to the server is meant to pull the internal state of the server for comparison with all connected clients. For easy integration, it may be assumed that the Testing Framework
@@
 an unique token to the client with which a socket connection can be requested. The client then requests entry into the game 
-with the token and a tunnel is established between the client and the server. Fig. 10 shows the game being played by three players, with
+with the token and a tunnel is established between the client and the server. Fig. 9 shows the game being played by three players, with
 the blue tank being controlled by the current instance.
@@
 communicate state changes over a two-way socket, the server also has several RESTful HTTP endpoints which allow connection negotiations and debugging data transfers to occur. 
-Fig. 11 showcases the architectural layout - note that in addition to the socket, the client may request some data over a HTTP call, and the server is then able to respond to 
+Fig. 10 showcases the architectural layout - note that in addition to the socket, the client may request some data over a HTTP call, and the server is then able to respond to 
 this call individually. The usefulness of this approach will become evident when attempting to inspect the internal state of the server.
@@
  The proposed implementation called for a testing library to be written, which caters to the peculiarities of a case such as NodeTank while providing generalized functionality for all 
- applications of the same architecture. Recall the class diagram in Fig 8. layed out the server-side and client-side classes utilized by the game. The authors have implemented a framework
+ applications of the same architecture. Recall the class diagram in Fig 7. layed out the server-side and client-side classes utilized by the game. The authors have implemented a framework
  under a class entity called "NodeTankTesting", which is coupled into one more more instances of the client-side. The applied changes are visualized in the Fig. 11 diagram. At a high-level,
@@
 After all of the ticks have been ran, we may leverage a debugging interface opened in the server(Listing 6, line 6), which returns the internal snapshot of the simulation from the server. 
-Using this snapshot, we will verify that the server copy of each tank's score, location and chat messages matches the authoritative snapshot. Putting it all together, we arrive at Fig. 15, which 
+Using this snapshot, we will verify that the server copy of each tank's score, location and chat messages matches the authoritative snapshot. Putting it all together, we arrive at Fig. 14, which 
 has all of the client instances performing the random actions and a representation of the test results. In this case, the framework has detected a discrepancy of Player 2's position on his own

### 2020-12-05 paper/PaperDraft2.tex

@@
 
-To be developed
-
 \subsection{Future Work}
-
+Future work would begin with a fully-realized implementation of the synthetic agent for, both, facilitating extended runtime data collection and testing as well as exploring the a fuller range of the game's runtime states.
+The testing utility would then include several pre-trained models minimally capable of navigating 2 and 3 dimensional environments while avoiding collisions with a generic interface for the tester(s) to provide functions specific to their environment for detecting states of collision as well as their reward signals unique to their environments.
 \section{References}

### 2020-12-05 paper/PaperDraft2.tex
Minor fix
Minor Paper Changes
CHanged the order of a figure
My Final paper update

@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics [width = 6cm, height = 9cm] {classv2.PNG}}
-\caption{Modified Class Diagram with Testing Framework}
-\end{figure}
-
 This testing framework relies on the ability to access the internal state of any client instance of NodeTank. The reader may be interested to know that the author of NodeTank 
@@
 mechanism utilized by languages such as Java, however we will continue to refer to them as classes as functionally they behave similarly enough.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics [width = 6cm, height = 9cm] {classv2.PNG}}
+\caption{Modified Class Diagram with Testing Framework}
+\end{figure}
 
@@
 
-\subsection{AutomatedFull-stack Testing}
+\subsection{Automated Full-stack Testing}
 
@@
 has all of the client instances performing the random actions and a representation of the test results. In this case, the framework has detected a discrepancy of Player 2's position on his own
-instance.
+instance. The reader is encouraged to download and run these test cases in order to see the dynamic control in action.
 
@@
 
+In conclusion, we have proposed and implemented several testing techniques for asynchronous certralized simulations. We have provided a generalized set of architectures which we then proceeded to 
+implement in NodeTank.
+In doing so, we have learned how to deal with asynchronous workflows and the tools necessary to implement new features into implementations of this type.
+In doing so, we not only providedthe reader with
+the requied knowledge to deal with testing centralized simulations, but the authors have also increased their knowledge base with the goal of continuing such research in the future.
+
 \subsection{Future Work}
